

Look at raw data
===========================================================================

First, let's load in all the data and plot the data from each year.

```{r, message = FALSE, warnings = FALSE}
library(dplyr)
looks1 <- readr::read_csv("./data-raw/rwl_timepoint1_looks.csv.gz")
looks2 <- readr::read_csv("./data-raw/rwl_timepoint2_looks.csv.gz")
looks3 <- readr::read_csv("./data-raw/rwl_timepoint3_looks.csv.gz")
looks <- bind_rows(looks1, looks2, looks3)

library(littlelisteners)
resp_def <- create_response_def(
  primary = "Target",
  others = c("PhonologicalFoil", "SemanticFoil", "Unrelated"),
  elsewhere = "tracked",
  missing = NA
)

raw_data <- looks %>% 
  filter(-505 <= Time, Time <= 2020, Version == "Standard") %>% 
  aggregate_looks(resp_def, Study + ResearchID + Time ~ GazeByImageAOI)
```

Make some plots of overall averages.

```{r raw-aim1, out.width = "50%", fig.show='hold', fig.height=3, fig.width=3}
library(ggplot2)

ggplot(raw_data) + 
  aes(x = Time, y = Prop, color = Study) +
  geom_hline(size = 2, color = "white", yintercept = .25) +
  stat_summary() +
  labs(x = "Time after target onset [ms]",
       y = "Proportion looks to target",
       caption = "Mean +/- SE") +
  theme_grey(base_size = 9) +
  theme(legend.position = c(0.05, 0.95), 
        legend.justification = c(0, 1))

ggplot(raw_data) + 
  aes(x = Time, y = Prop, color = Study) +
  geom_hline(size = 2, color = "white", yintercept = .25) +
  stat_smooth() +
  labs(x = "Time after target onset [ms]",
       y = "Proportion looks to target",
       caption = "GAM Smooth") +
  theme_grey(base_size = 9) +
  theme(legend.position = c(0.05, 0.95), 
        legend.justification = c(0, 1))
```

The raw data plainly confirm hypothesis 1:

> Children’s accuracy and efficiency of recognizing words will improve each year.

Look at a spaghetti plot...

```{r spaghetti-aim1, out.width = "100%", fig.height=2.5, fig.width=6}
ggplot(raw_data) + 
  aes(x = Time, y = Prop, group = ResearchID) +
  geom_hline(size = 2, color = "white", yintercept = .25) +
  geom_line(alpha = .15) +
  facet_grid(~ Study) +
  theme_grey(base_size = 9) +
  labs(x = "Time after target onset [ms]",
       y = "Proportion looks to target",
       caption = "Lines: Individual participants") +
  theme(legend.position = c(0.05, 0.95), 
        legend.justification = c(0, 1))
```



## Next up

Next up... Filter out bad trials. Filter out bad blocks. Make a table with a
head-count by study.

```{r}
missing_data_by_trial <- looks %>% 
  filter(-20 <= Time, Time <= 2020) %>% 
  aggregate_looks(
    resp_def, 
    Study + Version + ResearchID + Basename + TrialNo ~ GazeByImageAOI) %>% 
  mutate(BadTrial = .5 <= PropNA)

bad_trial_counts <- missing_data_by_trial %>% 
  count(Study, ResearchID, Basename, BadTrial) %>% 
  tidyr::spread(BadTrial, n) %>% 
  rename(n_bad = `TRUE`, n_good = `FALSE`) %>% 
  # Replace NAs with 0, in case there were 0 good trials in a block or 
  # 0 bad trials in a block
  mutate(n_bad = coalesce(n_bad, 0L),
         n_good = coalesce(n_good, 0L),
         trials = n_good + n_bad,
         prop_bad = round(n_bad / trials, 2)) 

blocks_to_drop <- bad_trial_counts %>% 
  filter(.5 <= prop_bad)
blocks_to_drop

leftover_bad_trials <- missing_data_by_trial %>% 
  anti_join(blocks_to_drop, by = c("Study", "ResearchID", "Basename")) %>% 
  filter(.5 <= PropNA)

clean_looks <- looks %>% 
  anti_join(blocks_to_drop, by = c("Study", "ResearchID", "Basename")) %>% 
  anti_join(leftover_bad_trials)
```


Plot the data after cleaning up trials.


```{r}
data <- clean_looks %>% 
  filter(-505 <= Time, Time <= 2020, Version == "Standard") %>% 
  aggregate_looks(resp_def, Study + ResearchID + Time ~ GazeByImageAOI)
```

We include the curves from the earlier plots in gray. The data-cleaning process 
slightly increases the average accuracy during the plateau-ed portion of the
growth curve.

```{r clean-aim1, out.width = "50%", fig.show='hold', fig.height=3, fig.width=3}
ggplot(data) + 
  aes(x = Time, y = Prop, color = Study) +
  geom_hline(size = 2, color = "white", yintercept = .25) +
  stat_summary(aes(group = Study), data = raw_data, 
               color = "gray70") +
  stat_summary() +
  labs(x = "Time after target onset [ms]",
       y = "Proportion looks to target",
       caption = "Mean +/- SE") +
  theme_grey(base_size = 9) +
  theme(legend.position = c(0.05, 0.95), 
        legend.justification = c(0, 1))

ggplot(data) + 
  aes(x = Time, y = Prop, color = Study) +
  geom_hline(size = 2, color = "white", yintercept = .25) +
  stat_smooth(aes(group = Study), data = raw_data, 
              color = "gray70") +
  stat_smooth() +
  labs(x = "Time after target onset [ms]",
       y = "Proportion looks to target",
       caption = "GAM Smooth") +
  theme_grey(base_size = 9) +
  theme(legend.position = c(0.05, 0.95), 
        legend.justification = c(0, 1))
```

