# Analyze familiar word recognition

Next steps:

- Model year over year changes.
- Download test scores and individual differences. 
- Model individual differences

```{r include = FALSE}
knitr::read_chunk("./helpers.R")
if (interactive()) source("./helpers.R")
```

```{r helpers, message = FALSE, warnings = FALSE}
```

Earlier we cleaned the data to remove trials with excessive missing data 
and blocks of trials with too few trials. Read in that data.

```{r, message = FALSE, warnings = FALSE}
data <- readr::read_csv("./data/aim1-screened.csv.gz")
```

Downsample into 50 ms bins.

```{r, eval = FALSE}
data <- data %>% 
  select(Study, ResearchID, TrialID:GazeByImageAOI) %>% 
  assign_bins(bin_width = 3, Time, TrialID)

# Compute time at center of each bin
bin_times <- data %>% 
  distinct(Time, .bin) %>% 
  group_by(.bin) %>% 
  mutate(BinTime = round(median(Time), -1)) %>% 
  ungroup()

# Attach bin times
binned <- data %>% 
  left_join(bin_times, by = c("Time", ".bin")) %>% 
  ungroup() %>% 
  select(-Time) %>% 
  rename(Time = BinTime) 

resp_def <- create_response_def(
  primary = "Target",
  others = c("PhonologicalFoil", "SemanticFoil", "Unrelated"),
  elsewhere = "tracked",
  missing = NA
)  
  
d <- binned %>% 
  aggregate_looks(resp_def, Study + ResearchID + Time ~ GazeByImageAOI)

d_m <- d %>% 
  filter(250 <= Time, Time <= 1500) %>% 
  polypoly::poly_add_columns(Time, degree = 3, 
                             scale_width = 1, prefix = "ot")
```

Plot the model-ready data. Use empirical logit because straight log-odds has too
high of values for plotting.

```{r}
ggplot(d_m) + 
  aes(x = Time, y = empirical_logit(Primary, Others)) + 
  geom_line(aes(group = ResearchID), alpha = .2) + 
  stat_smooth() +
  facet_grid(. ~ Study)
```

Fit a maximum likelihood model as a first pass. We won't fit the model
automatically. It's too time consuming. We save the results.

```{r, eval = FALSE}
library(lme4)
m <- glmer(
    cbind(Primary, Others) ~
      (ot1 + ot2 + ot3) * Study +
      (ot1 + ot2 + ot3 | ResearchID/Study),
    family = binomial,
    data = d_m)
summary(m)
readr::write_rds(m, "./data/aim1_cubic_model.rds.gz")
```

And reload them here.

```{r cubic-model-fits}
library(lme4)
m <- readr::read_rds("./data/aim1_cubic_model.rds.gz")
d_m$cubic_fit <- fitted(m)

ggplot(d_m) + 
  aes(x = Time, y = cubic_fit) + 
  geom_line(aes(group = ResearchID), alpha = .2) + 
  stat_smooth() +
  facet_grid(. ~ Study) + 
    labs(y = "Proportion looks to target [model fits]", 
       x = "Time afer noun onset [ms]")

top_10 <- m %>% 
  ranef() %>% 
  getElement("ResearchID") %>% 
  tibble::rownames_to_column("ResearchID") %>% 
  as_tibble() %>% 
  top_n(20, ot1) %>% 
  select(ResearchID, slope = ot1)

bot_10 <- m %>% 
  ranef() %>% 
  getElement("ResearchID") %>% 
  tibble::rownames_to_column("ResearchID") %>% 
  as_tibble() %>% 
  top_n(20, -ot1) %>% 
  select(ResearchID, slope = ot1)

okay <- m %>% 
  ranef() %>% 
  getElement("Study:ResearchID") %>% 
    tibble::rownames_to_column("ResearchID") %>% 
  as_tibble() %>% 
  tidyr::separate(ResearchID, c("Year", "ResearchID")) %>% 
  select(Year, ResearchID, ot1) %>% 
  tidyr::spread(Year, ot1) %>% 
  na.omit() %>% 
  mutate(y1 = rank(TimePoint1), 
         y2 = rank(TimePoint2), 
         y3 = rank(TimePoint3))
cor(okay[, -1], method =  "spearman")
summary(m)


ggplot(d_m) + 
  aes(x = Time, y = cubic_fit) + 
  geom_line(aes(group = ResearchID), alpha = .2) +
  geom_line(aes(group = ResearchID), data = semi_join(d_m, top_10), 
            size = .7, color = "#0074D9") + 
  geom_line(aes(group = ResearchID), data = semi_join(d_m, bot_10), 
            size = .7, color = "#FF4136") + 
  facet_grid(. ~ Study) + 
  labs(y = "Proportion looks to target [model fits]", 
       x = "Time afer noun onset [ms]")
ggsave("test.png")
ranks <- m %>% 
  ranef() %>% 
  getElement("ResearchID") %>% 
  tibble::rownames_to_column("ResearchID") %>% 
  as_tibble() %>% 
  mutate(rank = rank(ot1)) %>% 
  select(ResearchID, slope = rank)

# ggplot(inner_join(d_m, ranks),) + 
#   aes(x = Time, y = cubic_fit, color = -slope) + 
#   geom_line(aes(group = ResearchID), alpha = .4) +
#   viridis::scale_color_viridis() + 
#   facet_grid(. ~ Study)
  # geom_line(aes(group = ResearchID), data = semi_join(d_m, top_10), size = 1, color = "blue") + 
  # geom_line(aes(group = ResearchID), data = semi_join(d_m, bot_10), size = 1, color = "red") +
```


