# Visualize looks to each image type

We continue our exploration of the raw data by aggregating looks to each
image type. 

```{r include = FALSE}
knitr::read_chunk("./helpers.R")
if (interactive()) source("./helpers.R")
```

```{r helpers, include = FALSE}
```

Earlier we cleaned the data to remove trials with excessive missing data 
and blocks of trials with too few trials. Read in that data.

```{r, message = FALSE, warnings = FALSE, echo = FALSE, message = FALSE}
data <- readr::read_csv("./data/aim1-screened.csv.gz")

recode_studies <- tibble::tribble(
  ~S, ~S2, ~Study, ~Age,
  "TimePoint1", "TimePoint1", "TimePoint1", "Age 3",
  "TimePoint2", "TimePoint2", "TimePoint2", "Age 4",
  "TimePoint3", "TimePoint3", "TimePoint3", "Age 5",
)

convert_study_to_age <- function(xs) {
  factor(
    xs, 
    levels = c("TimePoint1", "TimePoint2", "TimePoint3"), 
    labels = c("Age 3", "Age 4", "Age 5"))
}
```

Plot growth curves to each AOI.

```{r by-aoi-prop, out.width = "100%", fig.height = 2.5, fig.width = 6, echo = FALSE, message = FALSE}
resp_def <- create_response_def(
  primary = "Target",
  others = c("PhonologicalFoil", "SemanticFoil", "Unrelated"),
  elsewhere = "tracked",
  missing = NA
)

defs <- cycle_response_def(resp_def)

# We use this later on
semy_defs <- defs %>% 
  purrr::keep(~ .x$primary %in% c("Target", "SemanticFoil")) 
phon_defs <- defs %>% 
  purrr::keep(~ .x$primary %in% c("Target", "PhonologicalFoil"))

# Aggregate looks using each rule
looks_by_aoi <- data %>% 
  aggregate_looks(defs, Study + ResearchID + Time ~ GazeByImageAOI) %>% 
  rename(AOI = .response_def) %>% 
  select(AOI:Time, Prop, Primary, Unrelated) %>% 
  mutate(
    AOI = AOI %>% 
      factor(c("Target", "PhonologicalFoil", "SemanticFoil", "Unrelated")))
  
ggplot(looks_by_aoi) + 
  aes(x = Time, y = Prop, color = Study) + 
  geom_hline(size = 2, color = "white", yintercept = .25) +
  stat_smooth(method = "gam", formula = y ~ s(x)) + 
  facet_grid( ~ AOI) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Proportion looking to image",
    caption = "GAM smooth") +
  theme_grey(base_size = 9) +
  theme(
    legend.position = c(0.95, 0.95), 
    legend.justification = c(1, 1))
```

The looks to target increase year over year which decreases the remaining
proportion of looks for the other three images each year. To study the relative
propensity of looking to each image, we instead can use the log-odds of looking
to each AOI versus the unrelated image.

```{r by-aoi-logit, out.width = "100%", fig.height = 2.5, fig.width = 6, echo = FALSE, message = FALSE}
ggplot(looks_by_aoi %>% filter(AOI != "Unrelated")) + 
  aes(x = Time, y = log(Primary / Unrelated), color = Study) + 
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth(method = "gam", formula = y ~ s(x)) + 
  facet_grid( ~ AOI) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking to word vs. unrelated word",
    caption = "GAM smooth") +
  theme_grey(base_size = 9) +
  theme(
    legend.position = c(0.95, 0.95), 
    legend.justification = c(1, 1))
```

Each curve is the log odds of looking to the target, phonological foil, and
semantic foil versus the unrelated word. Positive values mean more looks to an
image type than the unrelated. If you think of the _y_ axis as the image's
_relatedness_ to the target, you can see a time course of relatedness in each
panel: Here early phonological effects meaning early relatedness and later,
flatter semantic effects meaning late relatedness. (These effects make even more
sense sense if phonological representations affect processing before semantic
ones.)

This plot suggests an important finding: Children becoming more sensitive to the
phonological and semantic foils as they grow older. (I use the verb *suggest*
because this is still a preliminary, unmodeled finding.) Jan and I had made
opposite predictions about whether this would happen. Her argument, I think, was
that children become better at word recognition by becoming better able to
inhibit interference from competing words. This plot would suggest that they
show increased sensitive to the target and foils words by looking less to the
unrelated word as they age and reapportioning those looks to the other three
lexically relevant words.






## Comparing strong versus weak foils

In @RWLPaper, we ignored trials for certain items where we didn't think the
phonological or semantic similarity was strong enough. The two sets of
phonological foils are shown below.

```{r print-phon-foil-tables, message = FALSE, echo = FALSE}
trial_info <- bind_rows(
  readr::read_csv("data-raw/rwl_timepoint1_trials.csv.gz"),
  readr::read_csv("data-raw/rwl_timepoint2_trials.csv.gz"),
  readr::read_csv("data-raw/rwl_timepoint3_trials.csv.gz")) %>% 
  select(
    TrialID, 
    Target = WordTarget, 
    PhonologicalFoil = WordPhonologicalFoil,
    SemanticFoil = WordSemanticFoil, 
    Unrelated = WordUnrelated)

good_phono <- c("bear", "bee", "bell", "dress", "drum", "flag", "fly", 
                "heart", "horse", "pan", "pear", "pen", "vase")

good_semy <- c("bear", "bee", "bell", "bread", "cheese", "dress", 
               "drum", "fly", "horse", "pan", "pear", "shirt", "spoon")

words <- trial_info %>% 
  distinct(Target, PhonologicalFoil, SemanticFoil, Unrelated)

phono_foils <- split(words, words$Target %in% good_phono) %>% 
  lapply(arrange, Target) %>% 
  setNames(c("weak_foil", "strong_foil"))

semy_foils <- split(words, words$Target %in% good_semy) %>% 
  lapply(arrange, Target) %>% 
  setNames(c("weak_foil", "strong_foil"))

phono_foils$strong_foil %>% 
  knitr::kable(caption = "Trials with strong phonological foils.")

phono_foils$weak_foil %>% 
  knitr::kable(caption = "Trials with weak phonological foils.")
```

The stronger phonological foils are pairs where the syllable onsets are the
same. The weaker foils include rime pairs, pairs where the words have
different syllable onsets, and pairs where the onsets differ by a phonetic
feature.

```{r print-semy-foil-tables, message = FALSE, echo = FALSE}
semy_foils$strong_foil %>% 
  knitr::kable(caption = "Trials with strong semantic foils.")

semy_foils$weak_foil %>% 
  knitr::kable(caption = "Trials with weak semantic foils.")
```

The strong semantic foils belong to the same category and the weaker ones have a
less obvious relationship (*ring* and *dress*).

We visually confirm that the strong versus weak foils behave differently.

```{r by-aoi-logit-foils, out.width = "100%", fig.height = 2.5, fig.width = 6, echo = FALSE, message = FALSE}
weak_phon_looks <- trial_info %>% 
  semi_join(phono_foils$weak_foil) %>% 
  inner_join(data) %>% 
  mutate(PhonFoil = "Weak")

strong_phon_looks <- trial_info %>% 
  semi_join(phono_foils$strong_foil) %>% 
  inner_join(data) %>% 
  mutate(PhonFoil = "Strong")

phon_data <- bind_rows(strong_phon_looks, weak_phon_looks)

weak_semy_looks <- trial_info %>% 
  semi_join(semy_foils$weak_foil) %>% 
  inner_join(data) %>% 
  mutate(SemyFoil = "Weak")

strong_semy_looks <- trial_info %>% 
  semi_join(semy_foils$strong_foil) %>% 
  inner_join(data) %>% 
  mutate(SemyFoil = "Strong")

phon_data <- bind_rows(strong_phon_looks, weak_phon_looks)
semy_data <- bind_rows(weak_semy_looks, strong_semy_looks)

looks_by_aoi2 <- phon_data %>% 
  aggregate_looks(
    phon_defs, 
    Study + ResearchID + PhonFoil + Time ~ GazeByImageAOI) %>% 
  rename(AOI = .response_def) %>% 
  select(AOI:Time, PhonFoil, Prop, Primary, PhonologicalFoil, Unrelated) %>% 
  mutate(
    AOI = factor(
      AOI, c("Target", "PhonologicalFoil", "SemanticFoil", "Unrelated")))

looks_by_aoi3 <- semy_data %>% 
  aggregate_looks(
    semy_defs, Study + ResearchID + SemyFoil + Time ~ GazeByImageAOI) %>% 
  rename(AOI = .response_def) %>% 
  select(AOI:Time, SemyFoil, Prop, Primary, SemanticFoil, Unrelated) %>% 
  mutate(
    AOI = factor(
      AOI, c("Target", "PhonologicalFoil", "SemanticFoil", "Unrelated")))

ggplot(looks_by_aoi2 %>% filter(AOI != "Unrelated")) +
  aes(
    x = Time, y = log(Primary / Unrelated),
    color = Study, linetype = PhonFoil) +
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth(method = "gam", formula = y ~ s(x)) +
  facet_grid( ~ AOI) +
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking to word vs. unrelated word",
    caption = "GAM smooth on partially screened data") +
  theme_grey(base_size = 9)

ggplot(looks_by_aoi3 %>% filter(AOI != "Unrelated")) +
  aes(
    x = Time, y = log(Primary / Unrelated),
    color = Study, linetype = SemyFoil) +
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth(method = "gam", formula = y ~ s(x)) +
  facet_grid( ~ AOI) +
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking to word vs. unrelated word",
    caption = "GAM smooth on partially screened data") +
  theme_grey(base_size = 9)
```

What's going on here:

  - The weak phonological foils are indeed weaker than the strong foils.
  - The strong semantic foils appear stronger than the weak ones. The
    strong foils show a growth curve pattern of increasing looks away
    from baseline and there a developmental difference among the growth
    curves for each time point.
  - Children have a lower advantage for the target (vs unrelated) in
    weak foil trials because... why? My reading is that if the semantic
    or phonological foil is effective, children will look at it instead
    of the unrelated image. Conversely, if the semantic or phonological
    foil are less effective, children will look more to the unrelated
    image, which pulls down the ratio of looks to target versus the
    unrelated image.

In the above plots, we fixed the denominator to be the number of looks to the
unrelated image and varied the numerator. In the plots below, we fix the
numerator to be the looks to the target and vary the denominator to looks to
target versus looks to each foil.

```{r by-aoi-logit-target-phon, out.width = "100%", fig.height = 2.5, fig.width = 6, echo = FALSE, message = FALSE}
semantic_target_curves <- looks_by_aoi3 %>% 
  filter(AOI == "Target") %>% 
  mutate(
    `Target vs Semantic` = log(Primary / SemanticFoil), 
    `Target vs Unrelated` = log(Primary / Unrelated)) %>% 
  tidyr::gather(
    "Comparison", "LogOdds", 
    `Target vs Semantic`, `Target vs Unrelated`) 
  
phonological_target_curves <- looks_by_aoi2 %>% 
  filter(AOI == "Target") %>% 
  mutate(
    `Target vs Phonological` = log(Primary / PhonologicalFoil), 
    `Target vs Unrelated` = log(Primary / Unrelated)) %>% 
  tidyr::gather(
    "Comparison", "LogOdds", 
    `Target vs Phonological`, `Target vs Unrelated`) 
  
ggplot(phonological_target_curves) + 
  aes(x = Time, y = LogOdds, color = Study, linetype = PhonFoil) + 
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth(method = "gam", formula = y ~ s(x)) +
  facet_grid( ~ Comparison) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking",
    caption = "GAM smooth on partially screened data") +
  theme_grey(base_size = 9) 
```

Curves in both panels attain the same height, so phonological and unrelated
foils affect processing equally later in the trial. The strong phonological
foils curves in the Target vs Phonological comparison rise later than the weak
foils, reflecting early looks to the phonological foils.

```{r by-aoi-logit-target-semi, out.width = "100%", fig.height = 2.5, fig.width = 6, echo = FALSE, message = FALSE}
ggplot(semantic_target_curves) + 
  aes(x = Time, y = LogOdds, color = Study, linetype = SemyFoil) + 
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth(method = "gam", formula = y ~ s(x)) +
  facet_grid( ~ Comparison) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking",
    caption = "GAM smooth on partially screened data") +
  theme_grey(base_size = 9) 
```

Curves in the two panels do not attain the same height, so the semantic foil
reduces odds of fixating to the target later on in a trial. There appears to be
no difference in strong and weak foils in Year 2 and Year 3, so I might be able
to collapse to remove this distinction and include more items in the analysis.


```{r, echo = FALSE, results = "hide"}
opts_model <- list(
  bin_width = 3,
  start_time = 250,
  end_time = 1500
)
opts_model$bin_length <- round(opts_model$bin_width * 16.67, -1)
message("Modelling options: ")
message(str(opts_model))
```

## Looks to the phonological foil

```{r, echo = FALSE, message = FALSE}
data <- strong_phon_looks %>% 
  select(Study, ResearchID, TrialID:GazeByImageAOI) %>% 
  assign_bins(bin_width = opts_model$bin_width, Time, TrialID)

# Compute time at center of each bin
bin_times <- data %>% 
  distinct(Time, .bin) %>% 
  group_by(.bin) %>% 
  mutate(BinTime = round(median(Time), -1)) %>% 
  ungroup()

# Attach bin times
binned <- data %>% 
  left_join(bin_times, by = c("Time", ".bin")) %>% 
  ungroup() %>% 
  select(-Time) %>% 
  rename(Time = BinTime) 

d <- binned %>% 
  aggregate_looks(phon_defs, Study + ResearchID + Time ~ GazeByImageAOI)

phon_d <- d %>% 
  filter(
    opts_model$start_time <= Time, 
    Time <= opts_model$end_time) %>% 
  rename(Focus = .response_def)

# phon_d %>%
#   sample_n_of(9, ResearchID) %>%
#   ggplot() +
#     aes(
#       x = Time, y = log(Primary / Unrelated), 
#       color = Study, linetype = Focus) +
#     geom_line(aes(group = interaction(Study, Focus))) +
#     facet_wrap("ResearchID")
```

```{r, include = FALSE}
n_phon <- phono_foils$strong_foil$Target %>% unique() %>% length()
n_semy <- semy_foils$strong_foil$Target %>% unique() %>% length()
```

Next, we asked how children's sensitivity to the phonological foils
changed over developmental time. We only examined trials for which the
phonological foil and the noun shared the same syllable onset. For
example, this criterion included trials with *dress*–*drum*,
*fly*–*flag*, or *horse*–*heart*, but it excluded trials *kite*–*gift*
(feature difference), *bear*–*bread* (onset difference), and
*ring*–*swing* (rimes). We kept `r n_phon` of the 24 trials.

The outcome measure for these analyses was the log-odds of fixating on
the phonological foil versus the unrelated image. Because children
looked more to the target word with each year of the study, they
necessarily looked less to the distractors each year. Figure N below
illustrates how the proportions of looks to the phonological foils
declined each year. Therefore, we examined the effect of the
phonological foil in comparison to the unrelated foil. For example, on
the trials where the target is *fly*, we study the effect of the
phonological foil *flag* by looking at when and to what to degree the
children fixate on *flag* more than the unrelated image *pen*. If a
window of time of shows a consistent advantage for the phonological foil
over the unrelated image, we can conclude that the children were
sensitive to the phonological foil. By studying the time course of
fixations to the phonological foil versus the unrelated image, we can
identify when the phonological foil affected word recognition most
significantly.

As in the previous models, we downsampled the data into
`r opts_model$bin_length`-ms (`r opts_model$bin_width`-frame) bins in
order to smooth the data. We modeled the looks from
`r opts_model$start_time` to `r opts_model$end_time` ms. Lastly, we
aggregated looks by child, study and time.


```{r declining-phon-props, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5, fig.height = 3.5}
phon_d %>% 
  mutate(
    Focus = factor(
      Focus, c("Target", "PhonologicalFoil"), 
      c("Target", "Phonological foil")),
    Study = convert_study_to_age(Study)) %>% 
  ggplot() + 
    aes(x = Time, y = Prop, color = Study) + 
    geom_hline(yintercept = .25, color = "white", size = 2) +
    stat_summary(fun.y = "mean", geom = "line", size = 1) +
    facet_wrap("Focus") +
    labs(
      x = "Time after target onset [ms]",
      y = "Mean proportion looking to image") +
    theme_grey() +
    theme(
      legend.position = c(0.95, 0.95), 
      legend.justification = c(1, 1))
```

To account for the sparseness of the data, we used the empirical
log-odds (or empirical logit) transformation [@Barr2008]. This
transformation adds .5 to the looking counts. For example, a time-frame
with 4 looks to the phonological foil and 1 look to the unrelated image
has a conventional log-odds of log(4/1) = 1.39 and empirical log-odds of
log(4.5/1.5) = 1.10. This transformation fills in 0 values, and it
dampens the extremeness of some probabilities that arise in sparse count
data.

```{r, echo = FALSE, message = FALSE, include = FALSE, out.width = "80%", fig.width = 6}
library(mgcv)
library(itsadug)

phon_d <- phon_d %>% 
  mutate(
    S = factor(Study, c("TimePoint2", "TimePoint1", "TimePoint3")),
    R = as.factor(ResearchID),
    SR = interaction(S, R),
    elog = lookr::empirical_logit(PhonologicalFoil, Unrelated))

# Base model with no study effect
b2n <- bam(
  elog ~ s(Time), 
  data = phon_d, 
  method = "REML")
# summary(b2n)

# Include intercepts and smooths for studies
phon_d$S2 <- as.ordered(phon_d$S) 
contrasts(phon_d$S2) <- "contr.treatment"
contrasts(phon_d$S2)

# b2 <- bam(
#   elog ~ S + s(Time) + s(Time, by = S), 
#   data = phon_d, 
#   method = "REML")
# # summary(b2)

# b2_ordered <- bam(
#   elog ~ S2 + s(Time) + s(Time, by = S2),
#   data = phon_d,
#   method = "REML")
# summary(b2_ordered)
# plot(b2_ordered, pages = 1)

# b2r <- bam(
#   elog ~ S + s(Time) + s(Time, by = S) + s(Time, R, bs = "fs", m = 1, k = 5), 
#   data = phon_d)
# readr::write_rds(b2r, "./data/aim1-phon-random-smooths.rds.gz")
# b2r <- readr::read_rds("./data/aim1-phon-random-smooths.rds.gz")
# summary(b2r)
# plot(b2r, pages = 1)

# b2r_ordered <- bam(
#   elog ~ S2 + s(Time) + s(Time, by = S2) + s(Time, R, bs = "fs", m = 1, k = 5),
#   data = phon_d)


# plot(b2r_ordered2, pages = 1)
# readr::write_rds(b2r_ordered, "./data/aim1-phon-random-smooths2.rds.gz")
b2r_ordered <- readr::read_rds("./data/aim1-phon-random-smooths2.rds.gz")
summary(b2r_ordered)
# plot(b2r_ordered, pages = 1)
# report <- itsadug::report_stats(b2r)
# report[3, 2]
```

We fit a generalized additive model with fast restricted maximum
likelihood estimation [@Wood2017; @Soskuthy2017 for a tutorial for
linguists]. Box 1 provides a brief overview of these models. We fit the
models using the R package `mgcv` [vers. `r packageVersion("mgcv")`;
@Wood2017] with support from the tools in the `itsadug` package [vers.
`r packageVersion("itsadug")`; @itsadug].





\Begin{infobox}
<div class = "infobox">

**Box 1: The Intuition Behind Generalized Additive Models**.

In these analyses, the outcome of interest is a value that changes over
time in a nonlinear way. We model these time series by building a set of
features to represent time values. In the growth curve analyses of
familiar word recognition, we used a set of polynomial features which
expressed time as the weighted sum of a linear trend, a quadratic trend
and cubic trend. That is:

$$
\text{log-odds}(\mathit{looking}) = 
  \alpha + \beta_1 * \textit{Time}^1 +
           \beta_2 * \textit{Time}^2 +
           \beta_3 * \textit{Time}^3
$$

But another way to think about the polynomial terms is as *basis
functions*: A set of features that combine to approximate some nonlinear
function of time. Under this framework, the model can be expressed as:

$$
\text{log-odds}(\mathit{looking}) = 
  \alpha + f(\textit{Time})
$$
  
This is the idea behind generalized additive models and their *smooth
terms*. These smooths fit nonlinear functions of data by weighting and
adding simple functions together. The figures below show 9 basis
functions from a "thin-plate spline" and how they can be weighted and
summed to fit a growth curve.

```{r infobox-1-figs, message = FALSE, echo = FALSE, out.width = "66%", fig.width = 6, fig.height = 3}
library(mgcv)
library(ggplot2)
library(dplyr)

t1_fam <- structure(
  list(
    Time = c(
      250, 300, 350, 400, 450, 500, 550, 600, 650, 700, 750, 800, 850, 900, 
      950, 1000, 1050, 1100, 1150, 1200, 1250, 1300, 1350, 1400, 1450, 1500), 
    Prop = c(
      0.252, 0.255, 0.257, 0.261, 0.265, 0.275, 0.286, 0.298, 0.311, 0.315, 
      0.329, 0.342, 0.365, 0.392, 0.407, 0.422, 0.446, 0.464, 0.479, 0.497, 
      0.514, 0.524, 0.532, 0.545, 0.549, 0.555)), 
  .Names = c("Time", "Prop"), 
  class = c("tbl_df", "tbl", "data.frame"), 
  row.names = c(NA, -26L))

times <- modelr::seq_range(t1_fam$Time, 80)
newdata <- data.frame(Time = times)
t1_gam <- gam(Prop ~ s(Time), data = t1_fam)

t1_gam <- gam(Prop ~ s(Time, bs = "tp", k = 10), data = t1_fam)
basis_matrix <- predict(t1_gam, newdata, type = "lpmatrix")[, 2:10]

basis <- polypoly::poly_melt(basis_matrix) %>% 
  mutate(observation = as.numeric(observation)) %>% 
  left_join(
    data.frame(Time = times, observation = seq_along(times)), 
    by = "observation")

t1_poly <- lm(Prop ~ poly(Time, 3), data = t1_fam)

poly_basis <- polypoly::poly_melt(poly(t1_fam$Time, 3)) %>% 
  mutate(observation = as.numeric(observation)) %>% 
  left_join(
    data.frame(Time = times, observation = seq_along(times)), 
    by = "observation")

p1 <- ggplot(basis) + 
  aes(x = Time, y = value) + 
  geom_line(aes(color = degree)) + 
  ylim(c(-2, 2)) + 
  guides(color = FALSE) + 
  ggtitle("Basis functions (time features)") + 
  labs(y = NULL) +
  theme_grey(base_size = 9) + 
  theme(
    plot.background = element_rect(fill = "#eef7fa", colour = "#eef7fa"),
    panel.background = element_rect(fill = "#E5EAEF"))

p1_poly <- ggplot(poly_basis) + 
  aes(x = Time, y = value) + 
  geom_line(aes(color = degree)) + 
  # ylim(c(-2, 2)) + 
  guides(color = FALSE) + 
  ggtitle("Basis functions (time features)") + 
  labs(y = NULL) +
  theme_grey(base_size = 9)

weighted <- (basis_matrix %*% diag(coef(t1_gam)[-1])) %>% 
  polypoly::poly_melt() %>% 
  mutate(observation = as.numeric(observation)) %>% 
  left_join(
    data.frame(Time = times, observation = seq_along(times)), 
    by = "observation")

poly_weighted <- (poly(t1_fam$Time, 3) %*% diag(coef(t1_poly)[-1])) %>% 
  polypoly::poly_melt() %>% 
  mutate(observation = as.numeric(observation)) %>% 
  left_join(
    data.frame(Time = times, observation = seq_along(times)), 
    by = "observation")

p2 <- ggplot(weighted) + 
  aes(x = Time, y = value) + 
  geom_line(aes(color = factor(degree))) + 
  stat_summary(fun.y = sum, color = "#0074D9", geom = "line", size = 1.25) + 
  ylim(c(-.2, .2)) + 
  guides(color = FALSE) + 
  ggtitle("Weighted basis functions") + 
  labs(y = NULL) +
  theme_grey(base_size = 9)  + 
  theme(
    plot.background = element_rect(fill = "#eef7fa", colour = "#eef7fa"),
    panel.background = element_rect(fill = "#E5EAEF"))

p2_poly <- ggplot(poly_weighted) + 
  aes(x = Time, y = value) + 
  geom_line(aes(color = factor(degree))) + 
  stat_summary(fun.y = sum, color = "#0074D9", geom = "line", size = 1.25) + 
  ylim(c(-.2, .2)) + 
  guides(color = FALSE) + 
  ggtitle("Weighted basis functions") + 
  labs(y = NULL) +
  theme_grey(base_size = 9) 

p3 <- cowplot::plot_grid(p1, p2)
p3_poly <- cowplot::plot_grid(p1_poly, p2_poly)
print(p3)
# ggsave("./misc/basis-raw.png", p1,  width = 3, height = 3)
# ggsave("./misc/basis-weighted.png", p2, width = 3, height = 3)
# cowplot::ggsave("./misc/basis-both.png", p3, width = 6, height = 3)
# cowplot::ggsave("./misc/basis-both.png", p3, width = 6, height = 3)
```

Each of these basis functions is weighted by a model coefficient, but
the individual basis functions are not a priori meaningful. Rather, it
is the whole set of functions that approximate the curvature of the
data---i.e., *f*(Time))---so we statistically evaluate the whole batch
of coefficients simultaneously. This joint testing is similar to how one
might test a batch of effects in an ANOVA. If the batch of effects
jointly improve model fit, we infer that there is a significant smooth
or shape effect.

Smooth terms come with an estimated degrees of freedom (EDF). These
values provide a sense of how many degrees of freedom the smooth
consumed. An EDF of 1 is a perfectly straight line, indicating no
smoothing. Higher EDF values indicate that the smooth term captured more
curvature from the data.

<!-- The other important thing to know about generalized additive models is that -->
<!-- wigglyness is penalized. With so many functions, one might worry about -->
<!-- overfitting the data and including incidental wiggliness into *f*(Time). These -->
<!-- models, however, include a smoothing parameter that -->
</div>
\End{infobox}

The model included main effects of study year. These *parametric* terms
work like conventional regression effects and determined the growth
curve's average values. The model used age 4 as the reference year, so
the model's intercept represented the average looking probability at
age 4. The model's year effects therefore represented differences
between age 4 vs. age 3 and age 4 vs. age 5.

The model also included *smooth* terms to represent the time course of
the data. As with the parametric effects, age 4 served as the reference
year. The model estimated a smooth for age 4 and it estimated
*difference smooths* to capture how the curvature at age 3 and age 5
differed from the age 4 curvature. Each of these study-level smooths
used 10 knots (9 basis functions). We also included child-level *random
smooths* to represent child-level variation in growth curve shapes.
Because we have much as less data at the child level than at the study
level, these random smooths only included 5 knots (4 basis functions).
We can think of these simpler splines as coarse adjustments in growth
curve shape to capture child-level variation from limited data.
Altogether, the model contained the following terms:

```
emp. log-odds(phonological vs. unrelated) = 
  α + β1*Age-4 + β2*Age-5 +   [growth curve averages]
  f1(Time, Age-4) +           [reference smooth]
  f2(Time, Age-4 - Age-3) +   [difference smooths]
  f3(Time, Age-4 - Age-5) + 
  f4(Time, Child-ID)          [by-child random smooths]
```

```{r, echo = FALSE}
# prints p-value in markdown as "*p* < .001" or "*p* = [whatever]" 
format_p_value <- function(p, digits = 3) {
  formatted <- printy::fmt_p_value(p, digits)
  less_than <- stringr::str_detect(formatted, "<")
  if (less_than) {
    paste0("*p*&nbsp;", formatted)
  } else {
    paste0("*p*&nbsp;= ", formatted)
  }
}

b2r_summary <- summary.gam(b2r_ordered)

para <- b2r_summary$p.table %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("term") %>% 
  rename(estimate = Estimate, p.value = `Pr(>|t|)`)

tp2 <- para %>% 
  filter(term == "(Intercept)") %>% 
  pull(estimate) %>% 
  printy::fmt_fix_digits(2)

tp2_prop <- para %>% 
  filter(term == "(Intercept)") %>% 
  pull(estimate) %>% 
  plogis() %>% 
  printy::fmt_fix_digits(2) %>% 
  printy::fmt_leading_zero() 

tp1_p <- para %>% 
  filter(term == "S2TimePoint1") %>% 
  pull(p.value) %>% 
  format_p_value(digits = 2)

tp2_est <- para %>% 
  filter(term == "(Intercept)") %>% 
  pull(estimate) 

tp3_est <- para %>% 
  filter(term == "S2TimePoint3") %>% 
  pull(estimate) 

tp3_prop <- (tp2_est + tp3_est) %>% 
  plogis() %>% 
  printy::fmt_fix_digits(2) %>% 
  printy::fmt_leading_zero() 

tp3 <- (tp2_est + tp3_est) %>% 
  printy::fmt_fix_digits(2)

tp3_p <- para %>% 
  filter(term == "S2TimePoint3") %>% 
  pull(p.value) %>% 
  format_p_value()


# itsadug::report_stats(b2r_ordered, b2r_summary)
smooths <- b2r_summary$s.table %>% 
  as.data.frame() %>% 
  setNames(c("edf", "Ref.df", "F", "p.value")) %>% 
  tibble::rownames_to_column("term")

s_tp2_p <- smooths %>% 
  filter(term == "s(Time)") %>% 
  pull(p.value) %>% 
  format_p_value()

s_tp2_edf <- smooths %>% 
  filter(term == "s(Time)") %>% 
  pull(edf) %>% 
  printy::fmt_fix_digits(2)

s_tp1_edf <- smooths %>% 
  filter(term == "s(Time):S2TimePoint1") %>% 
  pull(edf) %>% 
  printy::fmt_fix_digits(2)

s_tp1_p <- smooths %>% 
  filter(term == "s(Time):S2TimePoint1") %>% 
  pull(p.value) %>% 
  format_p_value()

s_tp3_edf <- smooths %>% 
  filter(term == "s(Time):S2TimePoint3") %>% 
  pull(edf) %>% 
  printy::fmt_fix_digits(2)

s_tp3_p <- smooths %>% 
  filter(term == "s(Time):S2TimePoint3") %>% 
  pull(p.value) %>% 
  format_p_value()
```

The model’s fitted values are shown in
Figure \@ref(fig:phon-vs-unre-fits). These are the average empirical
log-odds of fixating on the phonological foil versus the unrelated image
for each year of the study. The model captured the trend for increased
looks to the competitor image with each year of the study. At age 4 and
age 5, the shape rises from a baseline to the peak around 800 ms. These
curves slope downwards and eventually fall beneath the initial baseline.
The shape at age 3 does not have a steady rise from baseline and shows a
very small peak around 800 ms.

(ref:phon-vs-unre-fits) Means for each year of the study estimated by
the generalized additive model. The left figure compares the model
estimates to the observed means and standard errors, and the right
figure visualizes the estimated means and their 95% confidence
intervals. With each year of the study, children looked increasingly
more to the phonological foil, relative to unrelated image, during and
after the target noun.

```{r phon-vs-unre-fits, fig.cap = "(ref:phon-vs-unre-fits)", echo = FALSE, warning = FALSE, message = FALSE, out.width = "80%", fig.width = 6, fig.height = 4, results = "hide"}
phon_d$fitted_elogit <- predict.gam(b2r_ordered)

p1 <- phon_d %>% 
  left_join(recode_studies, by = c("Study", "S", "S2")) %>% 
  ggplot() +
    aes(x = Time, y = fitted_elogit, color = Age) +
    geom_hline(size = 2, yintercept = 0, color = "white") +
    stat_summary(aes(y = elog), alpha = .7) +
    stat_summary(fun.y = "mean", geom = "line", size = 1) +
    coord_cartesian(ylim = c(-.35, .85)) +
    labs(
      x = "Time after target onset [ms]",
      y = "Emp. log-odds(Phon. vs. Unrelated)",
      caption = "Lines: Model fits. Points: Obs. means ± SE") +
    theme_grey(base_size = 10) +
    guides(color = FALSE) 

p2 <- b2r_ordered %>% 
  get_predictions(
    cond = list(
      Time = unique(phon_d$Time), 
      S2 = unique(phon_d$S2)),
    rm.ranef = TRUE) %>% 
  left_join(recode_studies) %>% 
  ggplot() + 
    aes(x = Time, y = fit, fill = Age) + 
    geom_hline(size = 2, yintercept = 0, color = "white") +
    geom_ribbon(aes(ymin = fit - CI, ymax = fit + CI), alpha = .2) +
    geom_line(aes(color = Age), size = 1) + 
    coord_cartesian(ylim = c(-.35, .85)) +
    labs(
      color = "Study",
      fill = "Study",
      x = "Time after target onset [ms]",
      y = NULL,
      caption = "Fitted means with 95% interval") + 
    theme_grey(base_size = 10) + 
    theme(
      legend.position = c(0.975, 0.975), 
      legend.justification = c(1, 1)) 

p3 <- cowplot::plot_grid(p1, p2)
print(p3)
```

The average looks to the phonological foil over the unrelated for age 4
was `r tp2` emp. log-odds, `r tp2_prop` proportion units. The averages
for age 3 and age 4 did not significantly differ, `r tp1_p` but the
average value was significantly greater at age 5, `r tp3` emp. log-odds,
`r tp3_prop` proportion units, `r tp3_p`. Visually, this effect shows up
in the almost constant height difference between the age-4 and the age-5
curves.

(ref:phon-diff-curves) Differences in the average looks to the
phonological foil versus the unrelated image between age 4 and the other
ages. Plotted line is estimated difference and the shaded region is
the 95% confidence around that difference. Blue boxes highlight regions
where the 95% interval excludes zero. From age 3 to age 4, children
become more sensitive to the phonological foil during and after the
target noun. The curves for age 3 and age 4 have largely the same shape,
but they steadily diverge over time.

```{r phon-diff-curves, fig.cap = "(ref:phon-diff-curves)", echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5, fig.height = 3, results = "hide"}
age5_age4 <- b2r_ordered %>% 
  get_difference(
    comp = list(S2 = c("TimePoint3", "TimePoint2")), 
    cond = list(Time = unique(phon_d$Time)), 
    rm.ranef = TRUE) %>% 
  mutate(comparison = "Age 5 − Age 4")
  
age4_age3 <- b2r_ordered %>% 
  get_difference(
    comp = list(S2 = c("TimePoint2", "TimePoint1")), 
    cond = list(Time = unique(phon_d$Time)), 
    rm.ranef = TRUE) %>% 
  mutate(comparison = "Age 4 − Age 3")  

rle_lengths <- function(xs) rle(xs)[["lengths"]]

differences <- bind_rows(age5_age4, age4_age3) %>% 
  rename(fit = difference) %>% 
  mutate(
    upper = fit + CI, 
    lower = fit - CI,
    no_zero = 0 > upper | 0 < lower) %>% 
  group_by(comparison) %>% 
  arrange(comparison, Time) %>% 
  mutate(
    streak = rep(seq_along(rle_lengths(no_zero)), rle_lengths(no_zero))) %>% 
  ungroup()

sig_regions <- differences %>% 
  filter(no_zero) %>% 
  group_by(comparison, streak) %>% 
  summarize(min = min(Time), max = max(Time)) %>% 
  ungroup()

ggplot(differences) + 
  aes(x = Time, y = fit) + 
  geom_hline(size = 2, yintercept = 0, color = "white") +
  geom_vline(
    aes(xintercept = min), data = sig_regions, 
    color = "blue", alpha = .5, linetype = "dashed") +
  geom_vline(
    aes(xintercept = max), data = sig_regions, 
    color = "blue", alpha = .5, linetype = "dashed") +
  geom_segment(
      aes(x = min, xend = max, group = streak), y = -Inf, yend = -Inf,
      data = sig_regions, color = "blue",  alpha = .5, size = 1) + 
  geom_segment(
      aes(x = min, xend = max, group = streak), y = Inf, yend = Inf,
      data = sig_regions, color = "blue",  alpha = .5, size = 1.1) + 
  geom_ribbon(aes(ymin = fit - CI, ymax = fit + CI), alpha = .2) +
  geom_line(size = 1) +
  labs(
    color = "Study",
    fill = "Study",
    x = "Time after target onset [ms]",
    y = "Difference in emp. log-odds",
    caption = "Estimated difference with 95% interval") + 
  facet_wrap("comparison")
```

There was a significant smooth term for time at age 4, estimated degrees
of freedom (EDF) = `r s_tp2_edf`, `r s_tp2_p`.
Figure \@ref(fig:phon-diff-curves) visualizes how and when the smooths
from other studies differed from the age-4 smooth.

The age-3 and age-4 significantly differed, EDF = `r s_tp1_edf`,
`r s_tp1_p`. In particular, the curves are significantly different
from 500 to 1050 ms. This result confirms that the looks to the
phonological foil increased from age 3 and age 4 during the time window
immediately following presentation of the noun. The similarity between
the phonological foil and the target occurs early in the trial. Given
the 150--300 ms time required to execute an eye movement in response to
speech, the time window for these differences indicates that children
became more sensitive to the phonological similarities between the foil
and the target from age 3 to age 4.

The age-3 and age-4 curves also differed significantly after 1250 ms.
The effect reflects how the looks to phonological foil decreased as the
trial progresses. After an incorrect look to the foil, the children on
average corrected their gaze and looked even less to the phonological
foil. We do not observe this degree of correction during age 3
presumably because children hardly looked to the phonological foil early
on.

The age-4 and age-5 smooths also significantly differed, EDF =
`r s_tp3_edf`, `r s_tp3_p`, although the low EDF values indicates that
the shape of the difference was a flat line. Thus, the difference
between the age-4 and age-5 smooths is driven primarily by the intercept
difference and a linear diverging trend---that is, the distance between
the two grows slightly over time. The same general curvature was
observed for the two studies, reflecting the same general looking
behavior at both time points. Children showed an early increase in looks
to the phonological foil relative to the unrelated image but after
receiving disqualifying information from the rest of the word, the looks
to the phonological foil rapidly decrease. The primary difference
between age-4 and age-5 is that the foil effect becomes more pronounced
at age 5.

Talking points:

  - Children increased their relative looks to the phonological foil with each
    year of the study. Although they looked to the target more quickly and more
    reliably with each of the study, the advantage of the phonological foil over
    the unrelated image increased with each year. Thus, the children became more
    sensitive to the phonological cohort words as they grew older.
  - There is hardly an effect of the phonological foil during timepoint 1. There
    are a few ways to interpret this finding. The first may be artefactual. The
    stimuli were re-recorded at timepoint 2 so the timepoint 1 stimuli were
    somewhat longer on average (around 800 ms at TP1 vs. 550--800ms later on).
    However, with slower stimuli, we would still expect an inflection in looks
    to the foil as children have more time to activate the phonological
    representations to the cohort. In other words, with more time to respond,
    there could plausibly be an even greater effect of early phonological
    information.
  - Alternatively, the children in timepoint 1 may not be using the early
    similarity of words during word recognition. That is, instead of immediate
    incremental activation of lexical cohorts, the children may not be
    activating the cohorts as reliably. This would imply that further study is
    required on the evidence for when young children begin to show immediate
    activation of cohorts.
  - The children at timepoint1 may not be incrementally activating the cohorts.
    The children in timepoint 2 and 3 certainly are.
  - Incremental activation and early commitments to partial information goes up 
    with age.


Here we have the data and the model fits.




```{r, results = "asis"}
itsadug::gamtabs(b2r_ordered, type = "html")
```









## Looks to the semantic foil

We used a similiar procedure on the looks to the semantic foil.

```{r}
n_semy <- semy_foils$strong_foil$Target %>% unique() %>% length()
```

Next, we asked how children's sensitivity to the semantic foils changed over
developmental time. We only examined trials for which the semantic foil and the
noun were part of the same category. We kept trials, for example, with
*bee*–*fly*, *shirt*–*dress*, or *spoon*–*pan*, but we excluded trials where
the similarity was perceptual (*sword*–*pen*) or too abstract (*swan*–*bee*). We
kept `r n_semy` of the 24 trials.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 6}
semy_data <- strong_semy_looks %>% 
  select(Study, ResearchID, TrialID:GazeByImageAOI) %>% 
  assign_bins(bin_width = opts_model$bin_width, Time, TrialID)

# Compute time at center of each bin
bin_times <- semy_data %>% 
  distinct(Time, .bin) %>% 
  group_by(.bin) %>% 
  mutate(BinTime = round(median(Time), -1)) %>% 
  ungroup()

# Attach bin times
binned <- semy_data %>% 
  left_join(bin_times, by = c("Time", ".bin")) %>% 
  ungroup() %>% 
  select(-Time) %>% 
  rename(Time = BinTime) 

semy_d <- binned %>% 
  aggregate_looks(semy_defs, Study + ResearchID + Time ~ GazeByImageAOI)

semy_d <- semy_d %>% 
  filter(250 <= Time, Time <= 1800) %>%
  rename(Focus = .response_def)

# semy_d %>%
#   sample_n_of(9, ResearchID) %>%
#   ggplot() +
#     aes(
#       x = Time, y = log(Primary / Unrelated), 
#       color = Study, linetype = Focus) +
#     geom_line(aes(group = interaction(Study, Focus))) +
#     facet_wrap("ResearchID")

semy_d <- semy_d %>% 
  mutate(
    S = factor(Study, c("TimePoint2", "TimePoint1", "TimePoint3")),
    R = as.factor(ResearchID),
    SR = interaction(S, R),
    elog = lookr::empirical_logit(SemanticFoil, Unrelated))

# Include intercepts and smooths for studies
semy_d$S2 <- as.ordered(semy_d$S) 
contrasts(semy_d$S2) <- "contr.treatment"
contrasts(semy_d$S2)

# Base model with no study effect
s2n <- bam(
  elog ~ s(Time), 
  data = semy_d)
# summary(b2n)

# Include intercepts and smooths for studies
s2 <- bam(
  elog ~ S2 + s(Time) + s(Time, by = S2), 
  data = semy_d)
summary(s2)
plot(s2, pages = 1)

s2r <- bam(
  elog ~ S2 + s(Time) + s(Time, by = S2) + s(Time, R, bs = "fs", m = 1, k = 5),
  data = semy_d)
# summary(s2r)
# plot(s2r, pages = 1)
# readr::write_rds(s2r, "./data/aim1-semy-random-smooths.rds.gz")
s2r <- readr::read_rds("./data/aim1-semy-random-smooths.rds.gz")
# gam.check(s2)
# anova(b2n, b2)

AIC(s2n, s2)
```

The model’s predictions are shown in the figure. It captured the trend for
increased looks to the competitor image with each year of the study.

```{r semy-vs-unre-fits, echo = FALSE, warning = FALSE, message = FALSE, out.width = "80%", fig.width = 5, fig.height = 4, results = "hide"}
itsadug::plot_smooth(s2r, view = "Time", plot_all = "S")

s2r %>% 
  get_predictions(
    cond = list(
      Time = unique(semy_d$Time), 
      S = unique(semy_d$S)),
    rm.ranef = TRUE) %>% 
  left_join(recode_studies) %>% 
  ggplot() + 
    aes(x = Time, y = fit, fill = Age) + 
    geom_hline(size = 2, yintercept = 0, color = "white") +
    geom_ribbon(aes(ymin = fit - CI, ymax = fit + CI), alpha = .2) +
    geom_line(aes(color = Age), size = 1) + 
    labs(
      color = "Study",
      fill = "Study",
      x = "Time after target onset [ms]",
      y = "Emp. log-odds(Sem. vs. Unrelated)",
      caption = "Fitted values with 95% interval") + 
    theme(
    legend.position = c(0.05, 0.95), 
    legend.justification = c(0, 1))

```

We also computed the difference of the curves from different studies. The
difference from timepoint 1 to timepoint 2 is just a matter of height.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5}
itsadug::plot_diff(
  s2,
  view = "Time",
  comp = list(S = c("TimePoint2", "TimePoint1")))
```

The difference from timepoint 2 to timepoint 3 includes a slight bump as the two
curves diverge from a similar starting position.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 4}
itsadug::plot_diff(
  s2,
  view = "Time",
  comp = list(S = c("TimePoint3", "TimePoint2")))
```

Timepoint 3 and timepoint 1 differ too. 

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5}
itsadug::plot_diff(
  s2,
  view = "Time",
  comp = list(S = c("TimePoint3", "TimePoint1")))
```

Here we have the data and the model fits.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 4}
semy_d$fitted_elogit <- predict.gam(s2)

ggplot(semy_d) +
  aes(x = Time, y = fitted_elogit, color = Study) +
  stat_summary(aes(y = elog)) +
  stat_summary(fun.y = "mean", geom = "line") +
  labs(
    y = "empirical logit",
    caption = "Lines: GAM fit. Point-ranges: Obs. Mean ± SE")
```


```{r semy-diff-curves, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5, fig.height = 3, results = "hide"}
age5_age4 <- s2r %>% 
  get_difference(
    comp = list(S = c("TimePoint3", "TimePoint2")), 
    cond = list(Time = unique(semy_d$Time)), 
    rm.ranef = TRUE) %>% 
  mutate(comparison = "Age 5 − Age 4")
  
age4_age3 <- s2r %>% 
  get_difference(
    comp = list(S = c("TimePoint2", "TimePoint1")), 
    cond = list(Time = unique(semy_d$Time)), 
    rm.ranef = TRUE) %>% 
  mutate(comparison = "Age 4 − Age 3")  

rle_lengths <- function(xs) rle(xs)[["lengths"]]

differences <- bind_rows(age5_age4, age4_age3) %>% 
  rename(fit = difference) %>% 
  mutate(
    upper = fit + CI, 
    lower = fit - CI,
    no_zero = 0 > upper | 0 < lower) %>% 
  group_by(comparison) %>% 
  arrange(comparison, Time) %>% 
  mutate(
    streak = rep(seq_along(rle_lengths(no_zero)), rle_lengths(no_zero))) %>% 
  ungroup()

sig_regions <- differences %>% 
  filter(no_zero) %>% 
  group_by(comparison, streak) %>% 
  summarize(min = min(Time), max = max(Time)) %>% 
  ungroup()

ggplot(differences) + 
  aes(x = Time, y = fit) + 
  geom_hline(size = 2, yintercept = 0, color = "white") +
  geom_vline(
    aes(xintercept = min), data = sig_regions, 
    color = "blue", alpha = .5, linetype = "dashed") +
  geom_vline(
    aes(xintercept = max), data = sig_regions, 
    color = "blue", alpha = .5, linetype = "dashed") +
  geom_segment(
      aes(x = min, xend = max, group = streak), y = -Inf, yend = -Inf,
      data = sig_regions, color = "blue",  alpha = .5, size = 1) + 
  geom_segment(
      aes(x = min, xend = max, group = streak), y = Inf, yend = Inf,
      data = sig_regions, color = "blue",  alpha = .5, size = 1.1) + 
  geom_ribbon(aes(ymin = fit - CI, ymax = fit + CI), alpha = .2) +
  geom_line(size = 1) +
  labs(
    color = "Study",
    fill = "Study",
    x = "Time after target onset [ms]",
    y = "Difference in emp. log-odds",
    caption = "Estimated difference with 95% interval") + 
  facet_wrap("comparison")


```






```{r, results = "asis"}
itsadug::gamtabs(s2, type = "html")
```








## Look for individual differences in competitor sensitivity

[...put this on hold for a while...]

<!-- Let's just run with all the foils. There's a trade-off here about sparsity and -->
<!-- strength of the stimuli. -->

```{r, eval = TRUE, out.width = "100%", echo = FALSE}
# ggplot(phon_d %>% filter(Focus == "PhonologicalFoil")) + 
#   aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
#   geom_line(aes(group = ResearchID), alpha = .2) + 
#   stat_smooth() +
#   facet_grid(. ~ Study)
# 
# ggplot(phon_d %>% filter(Focus == "PhonologicalFoil")) + 
#   aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
#   geom_line(aes(group = interaction(ResearchID, Study)), alpha = .2) + 
#   stat_smooth(aes(color = Study)) 
# 
# phon_d %>%
#   filter(Focus == "PhonologicalFoil") %>% 
#   sample_n_of(9, ResearchID) %>%
#   ggplot() + 
#     aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
#     geom_line(aes(group = interaction(ResearchID, Study)), alpha = .2) + 
#     stat_smooth(aes(color = Study)) +
#   facet_wrap("ResearchID")
# 
minp1 <- readr::read_csv("./data-raw/test_scores.csv") %>% 
  select(Study, ResearchID, MinPair_ProportionCorrect) %>% 
  filter(Study == "TimePoint1") %>% 
  mutate(
    MinP = ntile(MinPair_ProportionCorrect, 4),
    Cut = cut(MinPair_ProportionCorrect, c(0, .6, .8, 1))) %>% 
  select(-Study)

# table(minp1$Cut)
 
phon_d %>% 
  filter(Focus == "PhonologicalFoil") %>% 
  left_join(minp1) %>% 
  ggplot() + 
    aes(x = Time, y = plogis(empirical_logit(PhonologicalFoil, Unrelated))) + 
    geom_line(aes(group = ResearchID), alpha = .2) +
    stat_smooth(aes(color = Cut), se = FALSE) +
    facet_grid(. ~ Study)  + 
    ggtitle("To phon foil by minimal pairs")

phon_d %>% 
  filter(Focus == "Target") %>% 
  left_join(minp1) %>% 
  ggplot() + 
    aes(x = Time, y = Prop) + 
    geom_line(aes(group = ResearchID), alpha = .2) +
    stat_smooth(aes(color = Cut), se = FALSE) +
    facet_grid(. ~ Study) + 
   ggtitle("Prop to target by minimal pairs")

# phon_d %>% 
#   filter(Focus == "Target") %>% 
#   left_join(minp1) %>% 
#   ggplot() + 
#     aes(x = Time, y = plogis(empirical_logit(Target, Unrelated))) + 
#     geom_line(aes(group = ResearchID), alpha = .2) +
#     stat_smooth(aes(color = Cut), se = FALSE) +
#     facet_grid(. ~ Study)

# phon_d %>% 
#   filter(Focus == "PhonologicalFoil") %>% 
#   left_join(minp1) %>% 
#   ggplot() + 
#     aes(x = Time) + 
#     # geom_line(aes(group = ResearchID), alpha = .2) +
#     stat_smooth(
#       aes(color = Cut, y = plogis(empirical_logit(Target, PhonologicalFoil))), 
#       se = FALSE) +
#     stat_smooth(
#       aes(color = Cut, y = plogis(empirical_logit(Target, Unrelated))), 
#       se = FALSE, linetype = "dashed") +
#     facet_grid(Cut ~ Study)

# phon_d %>% 
#   filter(Focus == "Target") %>% 
#   left_join(minp1) %>% 
#   ggplot() + 
#     aes(x = Time, y = Prop) + 
#     geom_line(aes(group = ResearchID), alpha = .2) +
#     stat_smooth(aes(color = Cut), se = FALSE) +
#     facet_grid(. ~ Study)


evt1 <- readr::read_csv("./data-raw/test_scores.csv") %>% 
  select(Study, ResearchID, EVT_Standard) %>% 
  filter(Study == "TimePoint1") %>% 
  mutate(EVT = ntile(EVT_Standard, 4)) %>% 
  select(-Study)

# gfta1 <- readr::read_csv("./data-raw/scores_for_participant_summary.csv") %>% 
#   select(Study, ResearchID, GFTA_Standard) %>% 
#   filter(Study == "TimePoint1") %>% 
#   mutate(GFTA = ntile(GFTA_Standard, 4)) %>% 
#   select(-Study)


phon_d %>% 
  filter(Focus == "PhonologicalFoil") %>% 
  left_join(evt1) %>% 
  ggplot() + 
    aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
    geom_line(aes(group = ResearchID), alpha = .2) + 
    stat_smooth(aes(color = factor(EVT)), se = FALSE) +
    facet_grid(. ~ Study)

# phon_d %>% 
#   filter(Focus == "PhonologicalFoil") %>% 
#   left_join(gfta1) %>% 
#   ggplot() + 
#     aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
#     geom_line(aes(group = ResearchID), alpha = .2) + 
#     stat_smooth(aes(color = factor(GFTA)), se = FALSE) +
#     facet_grid(. ~ Study)



semy_d %>% 
  filter(Focus == "SemanticFoil") %>% 
  left_join(evt1) %>% 
  ggplot() + 
    aes(x = Time, y = empirical_logit(SemanticFoil, Unrelated)) + 
    geom_line(aes(group = ResearchID), alpha = .2) + 
    stat_smooth(aes(color = factor(EVT)), se = FALSE) +
    facet_grid(. ~ Study)

semy_d %>% 
  filter(Focus == "SemanticFoil") %>% 
  left_join(minp1) %>% 
  ggplot() + 
    aes(x = Time, y = empirical_logit(SemanticFoil, Unrelated)) + 
    geom_line(aes(group = ResearchID), alpha = .2) + 
    stat_smooth(aes(color = Cut), se = FALSE) +
    facet_grid(. ~ Study)

# m <- glmer(
#   cbind(PhonologicalFoil, Unrelated) ~ 
#     (ot1 + ot2 + ot3) * Study + 
#     (ot1 + ot2 + ot3 | ResearchID), 
#   family = binomial,
#   data = d_m)
# summary(m)
```
