# Visualize looks to each image type

We continue our exploration of the raw data by aggregating looks to each image 
type. 

```{r include = FALSE}
knitr::read_chunk("./helpers.R")
if (interactive()) source("./helpers.R")
```

```{r helpers, include = FALSE}
```

Earlier we cleaned the data to remove trials with excessive missing data 
and blocks of trials with too few trials. Read in that data.

```{r, message = FALSE, warnings = FALSE, echo = FALSE, message = FALSE}
data <- readr::read_csv("./data/aim1-screened.csv.gz")
```

Plot growth curves to each AOI.

```{r by-aoi-prop, out.width = "100%", fig.height=2.5, fig.width=6, echo = FALSE, message = FALSE}
resp_def <- create_response_def(
  primary = "Target",
  others = c("PhonologicalFoil", "SemanticFoil", "Unrelated"),
  elsewhere = "tracked",
  missing = NA
)

defs <- cycle_response_def(resp_def)

# We use this later on
semy_defs <- defs %>% 
  purrr::keep(~ .x$primary %in% c("Target", "SemanticFoil")) 
phon_defs <- defs %>% 
  purrr::keep(~ .x$primary %in% c("Target", "PhonologicalFoil"))

# Aggregate looks using each rule
looks_by_aoi <- data %>% 
  aggregate_looks(defs, Study + ResearchID + Time ~ GazeByImageAOI) %>% 
  rename(AOI = .response_def) %>% 
  select(AOI:Time, Prop, Primary, Unrelated) %>% 
  mutate(AOI = factor(AOI, c("Target", "PhonologicalFoil", 
                             "SemanticFoil", "Unrelated")))
  
ggplot(looks_by_aoi) + 
  aes(x = Time, y = Prop, color = Study) + 
  geom_hline(size = 2, color = "white", yintercept = .25) +
  stat_smooth() + 
  facet_grid( ~ AOI) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Proportion looking to image",
    caption = "GAM smooth") +
  theme_grey(base_size = 9) +
  theme(
    legend.position = c(0.95, 0.95), 
    legend.justification = c(1, 1))
```



The looks to target increase year over year which decreases the remaining
proportion of looks for the other three images each year. To study the relative
propensity of looking to each image, we instead can use the log-odds of looking
to each AOI versus the unrelated image.

```{r by-aoi-logit, out.width = "100%", fig.height=2.5, fig.width=6, echo = FALSE, message = FALSE}
ggplot(looks_by_aoi %>% filter(AOI != "Unrelated")) + 
  aes(x = Time, y = log(Primary / Unrelated), color = Study) + 
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth() + 
  facet_grid( ~ AOI) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking to word vs. unrelated word",
    caption = "GAM smooth") +
  theme_grey(base_size = 9) +
  theme(
    legend.position = c(0.95, 0.95), 
    legend.justification = c(1, 1))
```

Each curve is the log odds of looking to the target, phonological foil, and
semantic foil versus the unrelated word. Positive values mean more looks to an
image type than the unrelated. If you think of the _y_ axis as the image's
_relatedness_ to the target, you can see a time course of relatedness in each
panel: Here early phonological effects meaning early relatedness and later,
flatter semantic effects meaning late relatedness. (These effects make even more
sense sense if phonological representations affect processing before semantic
ones.)

This plot suggests an important finding: Children becoming more sensitive to the
phonological and semantic foils as they grow older. (I use the verb *suggest*
because this is still a preliminary, unmodeled finding.) Jan and I had made
opposite predictions about whether this would happen. Her argument, I think, was
that children become better at word recognition by becoming better able to
inhibit interference from competing words. This plot would suggest that they
show increased sensitive to the target and foils words by looking less to the
unrelated word as they age and reapportioning those looks to the other three
lexically relevant words.






## Comparing strong versus weak foils

In @RWLPaper, we ignored trials for certain items where we didn't think the
phonological or semantic similarity was strong enough. The two sets of
phonological foils are shown below.

```{r print-phon-foil-tables, message = FALSE, echo = FALSE}
trial_info <- bind_rows(
  readr::read_csv("data-raw/rwl_timepoint1_trials.csv.gz"),
  readr::read_csv("data-raw/rwl_timepoint2_trials.csv.gz"),
  readr::read_csv("data-raw/rwl_timepoint3_trials.csv.gz")) %>% 
  select(
    TrialID, Target = WordTarget, PhonologicalFoil = WordPhonologicalFoil,
    SemanticFoil = WordSemanticFoil, 
    Unrelated = WordUnrelated)

good_phono <- c("bear", "bee", "bell", "dress", "drum", "flag", "fly", 
                "heart", "horse", "pan", "pear", "pen", "vase")

good_semy <- c("bear", "bee", "bell", "bread", "cheese", "dress", 
               "drum", "fly", "horse", "pan", "pear", "shirt", "spoon")

words <- trial_info %>% 
  distinct(Target, PhonologicalFoil, SemanticFoil, Unrelated)

phono_foils <- split(words, words$Target %in% good_phono) %>% 
  lapply(arrange, Target) %>% 
  setNames(c("weak_foil", "strong_foil"))

semy_foils <- split(words, words$Target %in% good_semy) %>% 
  lapply(arrange, Target) %>% 
  setNames(c("weak_foil", "strong_foil"))

phono_foils$strong_foil %>% 
  knitr::kable(caption = "Trials with strong phonological foils.")

phono_foils$weak_foil %>% 
  knitr::kable(caption = "Trials with weak phonological foils.")
```

The stronger phonological foils are pairs where the syllable onsets are the
same. The weaker foils include rime pairs, pairs where the words have
different syllable onsets, and pairs where the onsets differ by a phonetic
feature.

```{r print-semy-foil-tables, message = FALSE, echo = FALSE}
semy_foils$strong_foil %>% 
  knitr::kable(caption = "Trials with strong semantic foils.")

semy_foils$weak_foil %>% 
  knitr::kable(caption = "Trials with weak semantic foils.")
```

The strong semantic foils belong to the same category and the weaker ones have a
less obvious relationship (*ring* and *dress*).

We visually confirm that the strong versus weak foils behave differently.

```{r by-aoi-logit-foils, out.width = "100%", fig.height = 2.5, fig.width = 6, echo = FALSE, message = FALSE}
weak_phon_looks <- trial_info %>% 
  semi_join(phono_foils$weak_foil) %>% 
  inner_join(data) %>% 
  mutate(PhonFoil = "Weak")

strong_phon_looks <- trial_info %>% 
  semi_join(phono_foils$strong_foil) %>% 
  inner_join(data) %>% 
  mutate(PhonFoil = "Strong")

phon_data <- bind_rows(strong_phon_looks, weak_phon_looks)

weak_semy_looks <- trial_info %>% 
  semi_join(semy_foils$weak_foil) %>% 
  inner_join(data) %>% 
  mutate(SemyFoil = "Weak")

strong_semy_looks <- trial_info %>% 
  semi_join(semy_foils$strong_foil) %>% 
  inner_join(data) %>% 
  mutate(SemyFoil = "Strong")

phon_data <- bind_rows(strong_phon_looks, weak_phon_looks)
semy_data <- bind_rows(weak_semy_looks, strong_semy_looks)

looks_by_aoi2 <- phon_data %>% 
  aggregate_looks(
    phon_defs, 
    Study + ResearchID + PhonFoil + Time ~ GazeByImageAOI) %>% 
  rename(AOI = .response_def) %>% 
  select(AOI:Time, PhonFoil, Prop, Primary, PhonologicalFoil, Unrelated) %>% 
  mutate(
    AOI = factor(
      AOI, c("Target", "PhonologicalFoil", "SemanticFoil", "Unrelated")))

looks_by_aoi3 <- semy_data %>% 
  aggregate_looks(
    semy_defs, Study + ResearchID + SemyFoil + Time ~ GazeByImageAOI) %>% 
  rename(AOI = .response_def) %>% 
  select(AOI:Time, SemyFoil, Prop, Primary, SemanticFoil, Unrelated) %>% 
  mutate(
    AOI = factor(
      AOI, c("Target", "PhonologicalFoil", "SemanticFoil", "Unrelated")))

ggplot(looks_by_aoi2 %>% filter(AOI != "Unrelated")) + 
  aes(
    x = Time, y = log(Primary / Unrelated), 
    color = Study, linetype = PhonFoil) + 
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth() + 
  facet_grid( ~ AOI) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking to word vs. unrelated word",
    caption = "GAM smooth on partially screened data") +
  theme_grey(base_size = 9) 

ggplot(looks_by_aoi3 %>% filter(AOI != "Unrelated")) + 
  aes(
    x = Time, y = log(Primary / Unrelated), 
    color = Study, linetype = SemyFoil) + 
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth() + 
  facet_grid( ~ AOI) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking to word vs. unrelated word",
    caption = "GAM smooth on partially screened data") +
  theme_grey(base_size = 9) 
```

What's going on here:

- The weak phonological foils are indeed weaker than the strong foils.
- The strong semantic foils appear stronger than the weak ones. The strong
  foils show a growth curve pattern of increasing looks away from baseline and
  there a developmental difference among the growth curves for each time
  point.
- Children have a lower advantage for the target (vs unrelated) in weak foil
  trials because... why? My reading is that if the semantic or phonological
  foil is effective, children will look at it instead of the unrelated image.
  Conversely, if the semantic or phonological foil are less effective,
  children will look more to the unrelated image, which pulls down the ratio
  of looks to target versus the unrelated image.

In the above plots, we fixed the denominator to be the number of looks to the
unrelated image and varied the numerator. In the plots below, we fix the
numerator to be the looks to the target and vary the denominator to looks to
target versus looks to each foil.

```{r by-aoi-logit-target-phon, out.width = "100%", fig.height=2.5, fig.width=6, echo = FALSE, message = FALSE}
semantic_target_curves <- looks_by_aoi3 %>% 
  filter(AOI == "Target") %>% 
  mutate(
    `Target vs Semantic` = log(Primary / SemanticFoil), 
    `Target vs Unrelated` = log(Primary / Unrelated)) %>% 
  tidyr::gather(
    "Comparison", "LogOdds", 
    `Target vs Semantic`, `Target vs Unrelated`) 
  
phonological_target_curves <- looks_by_aoi2 %>% 
  filter(AOI == "Target") %>% 
  mutate(
    `Target vs Phonological` = log(Primary / PhonologicalFoil), 
    `Target vs Unrelated` = log(Primary / Unrelated)) %>% 
  tidyr::gather(
    "Comparison", "LogOdds", 
    `Target vs Phonological`, `Target vs Unrelated`) 
  
ggplot(phonological_target_curves) + 
  aes(x = Time, y = LogOdds, color = Study, linetype = PhonFoil) + 
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth() + 
  facet_grid( ~ Comparison) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking",
    caption = "GAM smooth on partially screened data") +
  theme_grey(base_size = 9) 
```

Curves in both panels attain the same height, so phonological and unrelated foils 
affect processing equally later in the trial. The strong phonological foils 
curves in the Target vs Phonological comparison rise later than the weak foils, 
reflecting early looks to the phonological foils.

```{r by-aoi-logit-target-semi, out.width = "100%", fig.height=2.5, fig.width=6, echo = FALSE, message = FALSE}
ggplot(semantic_target_curves) + 
  aes(x = Time, y = LogOdds, color = Study, linetype = SemyFoil) + 
  geom_hline(size = 2, color = "white", yintercept = 0) +
  stat_smooth() + 
  facet_grid( ~ Comparison) + 
  labs(
    x = "Time after target onset [ms]",
    y = "Log odds looking",
    caption = "GAM smooth on partially screened data") +
  theme_grey(base_size = 9) 
```

Curves in the two panels do not attain the same height, so the semantic foil
reduces odds of fixating to the target later on in a trial. There appears to be
no difference in strong and weak foils in Year 2 and Year 3, so I might be able
to collapse to remove this distinction and include more items in the analysis.


## Preparing data for the model

```{r, echo = FALSE}
opts_model <- list(
  bin_width = 3,
  start_time = 250,
  end_time = 1500
)
opts_model$bin_length <- round(opts_model$bin_width * 16.67, -1)
message("Modelling options: ")
message(str(opts_model))
```

As in the earlier models, we downsampled the data into
`r opts_model$bin_length`-ms (`r opts_model$bin_width`-frame) bins in order to
smooth the data. We modeled the looks from `r opts_model$start_time` to
`r opts_model$end_time` ms. Lastly, we aggregated looks by child, study and
time, and created orthogonal polynomials to use as time features for the model


```{r, echo = FALSE, message = FALSE}
data <- strong_phon_looks %>% 
  select(Study, ResearchID, TrialID:GazeByImageAOI) %>% 
  assign_bins(bin_width = opts_model$bin_width, Time, TrialID)

# Compute time at center of each bin
bin_times <- data %>% 
  distinct(Time, .bin) %>% 
  group_by(.bin) %>% 
  mutate(BinTime = round(median(Time), -1)) %>% 
  ungroup()

# Attach bin times
binned <- data %>% 
  left_join(bin_times, by = c("Time", ".bin")) %>% 
  ungroup() %>% 
  select(-Time) %>% 
  rename(Time = BinTime) 

d <- binned %>% 
  aggregate_looks(phon_defs, Study + ResearchID + Time ~ GazeByImageAOI)

phon_d <- d %>% 
  filter(
    opts_model$start_time <= Time, 
    Time <= opts_model$end_time) %>% 
  polypoly::poly_add_columns(
    Time, degree = 3, scale_width = 1, prefix = "ot") %>% 
  rename(Focus = .response_def)

phon_d %>%
  sample_n_of(9, ResearchID) %>%
  ggplot() +
    aes(
      x = Time, y = log(Primary / Unrelated), 
      color = Study, linetype = Focus) +
    geom_line(aes(group = interaction(Study, Focus))) +
    facet_wrap("ResearchID")


```

The final model should looks like this. I'll have to run this for a few days.

```{r, eval = FALSE}
# phon_d <- phon_d %>% 
#   filter(Focus == "PhonologicalFoil")
# 
# library(rstanarm)
# options(mc.cores = parallel::detectCores())
# 
# m <- stan_glmer(
#  cbind(Primary, Unrelated) ~ 
#         Study * (ot1 + ot2 + ot3) + 
#         (ot1 + ot2 + ot3 | ResearchID) + 
#         (ot1 + ot2 + ot3 | Study:ResearchID),
#   family = binomial,
#   prior = normal(0, 1, autoscale = FALSE),
#   prior_intercept = normal(0, 2),
#   prior_covariance = decov(2, 1, 1),
#   control = list(adapt_delta = .99),
#   data = phon_d)
# readr::write_rds(m, "./data/stan_aim1_phon_model2.rds.gz")
```

For this model structure, we estimate two growth curves simultaneously for each
year of the study. Each growth curve is the log-odds of fixating on a certain
image relative to the unrelated image. We use an indicator variable *focus* to
record whether the image is the target or the phonological foil. 

Actually, I am not sure I need to estimate two growth curves simulataneously
yet. I could just estimate log-odds of looking to Phonological vs Unrelated
directly. This would let me estimate year over year changes, the time course of
the effects and maybe some individual differences in looks to the phonological
foil. I could posterior-predict looks at each time bin and see how the 
intervals compare to zero.


Hmmm, this is not working quite right yet.

```{r, eval = FALSE, echo = FALSE}
# library(rstanarm)
# okay <- readr::read_rds("./data/stan_aim1_phon_model2.rds.gz")
# summary(okay, pars = names(fixef(okay)))
# 
# sims <- rstanarm::posterior_predict(okay, draws = 200, seed = "09272017")
# n_trials <- data_frame(y_id = seq_along(okay$y[, 1]), n_trials = rowSums(okay$y))
# 
# length(phon_d$Study)
# length(okay$y[, 1])
# 
# bayesplot:::ppc_data(okay$y[, 1], sims, group = phon_d$Study) %>% 
#   left_join(n_trials, by = "y_id") %>% 
#   mutate(prop = value / n_trials) %>% 
#   ggplot() +
#     aes(x = prop) +
#     stat_density(
#       aes_(group = ~ rep_id),
#       data = function(x) dplyr::filter(x, !.data$is_y),
#       geom = "line", position = "identity", size = .25, alpha = .1, 
#       color = "#0074D9") +
#     stat_density(
#       data = function(x) dplyr::filter(x, .data$is_y),
#       geom = "line", position = "identity", size = 1) + 
#     labs(x = "Proportion of looks", 
#          title = "Observed data and 200 posterior simulations") + 
#     coord_cartesian(xlim = c(0, 1), expand = FALSE) + 
#     facet_wrap("group")
```


## Looks to the phonological foil

```{r}
n_phon <- phono_foils$strong_foil$Target %>% unique() %>% length()
n_semy <- semy_foils$strong_foil$Target %>% unique() %>% length()
```

Next, we asked how children's sensitivity to the phonological foils changed over
developmental time. We only examined trials for which the phonological foil and
the noun shared the same syllable onset. For example, we kept trials with
*dress*–*drum*, *fly*–*flag*, or *horse*–*heart*, but we excluded trials
*kite*–*gift* (feature difference), *bear*–*bread* (onset difference), and
*ring*–*swing* (rimes). We kept `r n_phon` of the 24 trials.

Because children looked more to the target word with each year of the study,
they necessarily looked less to the distractors each year.

```{r, echo = FALSE, message = FALSE, out.width = "100%", fig.width = 4}
phon_d %>% 
  mutate(Focus = factor(Focus, c("Target", "PhonologicalFoil"))) %>% 
  ggplot() + 
    aes(x = Time, y = Prop, color = Study) + 
    geom_hline(yintercept = .25, color = "white", size = 2) +
    stat_summary() + 
    facet_wrap("Focus") +
    labs(
      x = "Time after target onset [ms]",
      y = "Proportion looking to image",
      caption = "Mean +/- SE") +
    theme_grey() +
    theme(
      legend.position = c(0.95, 0.95), 
      legend.justification = c(1, 1))
```

To account for the sparseness of the data, we used the empirical logit
transformation [refs]. This transformation adds .5 to the looking counts. For
example, a time-frame with 4 looks to the phonological foil and 1 look to the
foil has (conventional) logit of log(4/1) = 1.39 and empirical logit of log(4.5/1.5) = 1.10.
This transformation fills in 0 values, and it dampens the extremeness of some
probabilities that happen in sparse count data.


```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 6}
library(mgcv)
library(itsadug)

phon_d <- phon_d %>% 
  mutate(
    S = factor(Study, c("TimePoint2", "TimePoint1", "TimePoint3")),
    R = as.factor(ResearchID),
    SR = interaction(S, R),
    elog = lookr::empirical_logit(PhonologicalFoil, Unrelated))

# Base model with no study effect
b2n <- gam(
  elog ~ s(Time), 
  data = phon_d, 
  method = "REML")
# summary(b2n)

# Include intercepts and smooths for studies
b2 <- gam(
  elog ~ S + s(Time) + s(Time, by = S), 
  data = phon_d, 
  method = "REML")
summary(b2)

# b2r <- bam(
#   elog ~ S + s(Time) + s(Time, by = S) + s(Time, R, bs = "fs", m = 1, k = 5), 
#   data = phon_d)
# readr::write_rds(b2r, "./data/aim1-phon-random-smooths.gz")
b2r <- readr::read_rds("./data/aim1-phon-random-smooths.gz")
summary(b2r)

plot(b2r, pages = 1)
```



We fit a generalized additive model with restricted maximum likelihood
[@Wood2017; @Soskuthy2017 for a tutorial for linguists; see Box 1]. 
We included main-effects of study year. These parametric terms work like
conventional regression effects and determined the growth curve's average
values. We used timepoint 2 as the reference year, so the model's intercept
represented the average looking probability for timepoint 2. The model's year
effects therefore represented differences between timepoint 2 vs. timepoint 1
and vs. timepoint 3.

```{block2, type = "infobox"}
**Box 1: The Intuition Behind Generalized Additive Models**.

[work in progress]

In these analyses, the outcome of interest is a value that changes over time in
a nonlinear way. We model these time series by building a set of features, or a
*basis*, to represent time values. In the familiar word recognition analyses, we
used a polynomial basis which expressed time as the weighted sum of a linear
trend, a quadratic trend and cubic trend. That is:

P(to target) = α + β1*Linear + β2*Quadratic + β3*Cubic [growth curve averages] 

But another way to think about the polynomial terms is as a basis: A set of
features that work together to approximate a nonlinear functio of time. Under
this framework, the model might be described as:

P(to target) = α + f(Time)

This is the way to think about generalized additive models. These fit nonlinear
functions of predictor variables by using *smooth* terms. These smooth terms fit
nonlinear functions of data by weighting and adding small bumps (splines)
together---hence the name additive models.

(plot of splines and weighted splines approximating a curve)
```

We also included smooth terms for time. These smooth terms fit nonlinear
functions of data by weighting and adding small bumps (splines) together---hence
the name additive models. We included a smooth term for trial time to represent
a general effect of time following noun onset across all studies, and we also
included smooth terms for time for each study. As an equation, our model
estimated:

```
emp. logit(phonological vs unrelated) = 
  α + β1*Study1 + β2*Study3 +   [growth curve averages]
  f1(Time) +                    [general shape]
  f2(Time, Study1) +            [study-specific shapes]
  f3(Time, Study2) + 
  f4(Time, Study3)      
```

```{r, echo = FALSE}
para <- broom::tidy(b2, parametric = TRUE) 

tp2 <- para %>% 
  filter(term == "(Intercept)") %>% 
  pull(estimate) %>% 
  printy::fmt_fix_digits(2)

tp2_prop <- para %>% 
  filter(term == "(Intercept)") %>% 
  pull(estimate) %>% 
  plogis() %>% 
  printy::fmt_fix_digits(2) %>% 
  printy::fmt_leading_zero() 

tp1_p <- para %>% 
  filter(term == "STimePoint1") %>% 
  pull(p.value) %>% 
  printy::fmt_p_value(digits = 2)

tp2_est <- para %>% 
  filter(term == "(Intercept)") %>% 
  pull(estimate) 

tp3_est <- para %>% 
  filter(term == "STimePoint3") %>% 
  pull(estimate) 

tp3_prop <- (tp2_est + tp3_est) %>% 
  plogis() %>% 
  printy::fmt_fix_digits(2) %>% 
  printy::fmt_leading_zero() 

tp3 <- (tp2_est + tp3_est) %>% 
  printy::fmt_fix_digits(2)

tp3_p <- para %>% 
  filter(term == "STimePoint3") %>% 
  pull(p.value) %>% 
  printy::fmt_p_value()
```

The model’s predictions are shown in the figure. It captured the trend for
increased looks to the competitor image with each year of the study. [describe
the shape some more]

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5}
itsadug::plot_smooth(b2, view = "Time", plot_all = "S")
```

The average looks to the phonological foil over the unrelated for timepoint 2
was `r tp2` emp. logits, `r tp2_prop` proportion units. The averages for
timepoint 1 and timepoint 2 did not significantly differ, *p* = `r tp1_p`, but
the average value was significantly greater at timepoint 3, `r tp3` emp. logits,
`r tp3_prop` proportion units, *p* `r tp1_p`.

```{r}
anova(b2r)
```

Each smooth term represents a batch of coefficients. Each coefficient in a
smooth contributes to the shape of the curve, so the coefficients are
tested jointly like a batch of effects in an ANOVA. There was a significant
smooth term for time in general, (f-test stats) and for timepoint 1, (f-test
stats). In contrast, the smooths timepoint 2 and timepoint 3 did not differ
significantly from the general time smooth, (p timepoint2), (p timepoint2). 
Thus, timepoint 2 and timepoint 3 had essentially the same same shape, the
observed difference stemming from the timepoint 3 being higher on average.

We also computed the difference of the curves from different studies. The peaks
of the timepoint 1 and timepoint 2 were significantly different from 500 to 1045
ms. This result confirms that the looks to the phonological foil increased from
timepoint 1 and timepoint 2 in the time window immediately following
presentation of the noun. [The difference at the end...]

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5}
itsadug::plot_diff(
  b2r,
  view = "Time",
  comp = list(S = c("TimePoint2", "TimePoint1")))
```

The difference between the timepoint 2 and the timepoint 3 smooths is driven by
the the intercept difference. The difference line between the two is a straight
line. The two curves start from the same location and diverge, and that's what
this straight line captures.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5}
itsadug::plot_diff(
  b2r,
  view = "Time",
  comp = list(S = c("TimePoint3", "TimePoint2")))
```

Timepoint 3 and timepoint 1 differ too. 

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5}
itsadug::plot_diff(
  b2r,
  view = "Time",
  comp = list(S = c("TimePoint3", "TimePoint1")))
```

Here we have the data and the model fits.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 6}
phon_d$fitted_elogit <- predict.gam(b2r)

ggplot(phon_d) +
  aes(x = Time, y = fitted_elogit, color = Study) +
  stat_summary(aes(y = elog)) +
  stat_summary(fun.y = "mean", geom = "line") +
  labs(
    y = "empirical logit",
    caption = "Lines: GAM fit. Point-ranges: Obs. Mean ± SE")
```

Talking points:

  - The children at timepoint1 may not be incrementally activating the cohorts.
    The children in timepoint 2 and 3 certainly are.
  - Incremental activation and early commitments to partial information goes up 
    with age.

```{r, results = "asis"}
itsadug::gamtabs(b2r, type = "html")
```









## Looks to the semantic foil

We used a similiar procedure on the looks to the semantic foil.

```{r}
n_semy <- semy_foils$strong_foil$Target %>% unique() %>% length()
```

Next, we asked how children's sensitivity to the semantic foils changed over
developmental time. We only examined trials for which the semantic foil and the
noun were part of the same category. We kept trials, for example, with
*bee*–*fly*, *shirt*–*dress*, or *spoon*–*pan*, but we excluded trials where
the similarity was perceptual (*sword*–*pen*) or too abstract (*swan*–*bee*). We
kept `r n_semy` of the 24 trials.


```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 6}
semy_data <- strong_semy_looks %>% 
  select(Study, ResearchID, TrialID:GazeByImageAOI) %>% 
  assign_bins(bin_width = opts_model$bin_width, Time, TrialID)

# Compute time at center of each bin
bin_times <- semy_data %>% 
  distinct(Time, .bin) %>% 
  group_by(.bin) %>% 
  mutate(BinTime = round(median(Time), -1)) %>% 
  ungroup()

# Attach bin times
binned <- semy_data %>% 
  left_join(bin_times, by = c("Time", ".bin")) %>% 
  ungroup() %>% 
  select(-Time) %>% 
  rename(Time = BinTime) 

semy_d <- binned %>% 
  aggregate_looks(semy_defs, Study + ResearchID + Time ~ GazeByImageAOI)

semy_d <- semy_d %>% 
  filter(
    250 <= Time,
    Time <= 1800
  ) %>%
  # polypoly::poly_add_columns(
  #   Time, degree = 3, scale_width = 1, prefix = "ot") %>% 
  rename(Focus = .response_def)

semy_d %>%
  sample_n_of(9, ResearchID) %>%
  ggplot() +
    aes(
      x = Time, y = log(Primary / Unrelated), 
      color = Study, linetype = Focus) +
    geom_line(aes(group = interaction(Study, Focus))) +
    facet_wrap("ResearchID")

semy_d <- semy_d %>% 
  mutate(
    S = factor(Study, c("TimePoint2", "TimePoint1", "TimePoint3")),
    R = as.factor(ResearchID),
    SR = interaction(S, R),
    elog = lookr::empirical_logit(SemanticFoil, Unrelated))

# Base model with no study effect
s2n <- gam(
  elog ~ s(Time), 
  data = semy_d, 
  method = "REML")
# summary(b2n)

# Include intercepts and smooths for studies
s2 <- gam(
  elog ~ S + s(Time) + s(Time, by = S), 
  data = semy_d, 
  method = "REML")
summary(s2)
plot(s2, pages = 1)
# gam.check(s2)
# anova(b2n, b2)

AIC(s2n, s2)
```

The model’s predictions are shown in the figure. It captured the trend for
increased looks to the competitor image with each year of the study.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5}
itsadug::plot_smooth(s2, view = "Time", plot_all = "S")
```

We also computed the difference of the curves from different studies. The
difference from timepoint 1 to timepoint 2 is just a matter of height.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5}
itsadug::plot_diff(
  s2,
  view = "Time",
  comp = list(S = c("TimePoint2", "TimePoint1")))
```

The difference from timepoint 2 to timepoint 3 includes a slight bump as the two
curves diverge from a similar starting position.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 4}
itsadug::plot_diff(
  s2,
  view = "Time",
  comp = list(S = c("TimePoint3", "TimePoint2")))
```

Timepoint 3 and timepoint 1 differ too. 

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 5}
itsadug::plot_diff(
  s2,
  view = "Time",
  comp = list(S = c("TimePoint3", "TimePoint1")))
```

Here we have the data and the model fits.

```{r, echo = FALSE, message = FALSE, out.width = "80%", fig.width = 4}
semy_d$fitted_elogit <- predict.gam(s2)

ggplot(semy_d) +
  aes(x = Time, y = fitted_elogit, color = Study) +
  stat_summary(aes(y = elog)) +
  stat_summary(fun.y = "mean", geom = "line") +
  labs(
    y = "empirical logit",
    caption = "Lines: GAM fit. Point-ranges: Obs. Mean ± SE")
```







```{r, results = "asis"}
itsadug::gamtabs(s2, type = "html")
```








## Look for individual differences in competitor sensitivity

[...put this on hold for a while...]

<!-- Let's just run with all the foils. There's a trade-off here about sparsity and -->
<!-- strength of the stimuli. -->

```{r, eval = TRUE, out.width = "100%", echo = FALSE}
# ggplot(phon_d %>% filter(Focus == "PhonologicalFoil")) + 
#   aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
#   geom_line(aes(group = ResearchID), alpha = .2) + 
#   stat_smooth() +
#   facet_grid(. ~ Study)
# 
# ggplot(phon_d %>% filter(Focus == "PhonologicalFoil")) + 
#   aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
#   geom_line(aes(group = interaction(ResearchID, Study)), alpha = .2) + 
#   stat_smooth(aes(color = Study)) 
# 
# phon_d %>%
#   filter(Focus == "PhonologicalFoil") %>% 
#   sample_n_of(9, ResearchID) %>%
#   ggplot() + 
#     aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
#     geom_line(aes(group = interaction(ResearchID, Study)), alpha = .2) + 
#     stat_smooth(aes(color = Study)) +
#   facet_wrap("ResearchID")
# 
minp1 <- readr::read_csv("./data-raw/test_scores.csv") %>% 
  select(Study, ResearchID, MinPair_ProportionCorrect) %>% 
  filter(Study == "TimePoint1") %>% 
  mutate(
    MinP = ntile(MinPair_ProportionCorrect, 4),
    Cut = cut(MinPair_ProportionCorrect, c(0, .6, .8, 1))) %>% 
  select(-Study)

# table(minp1$Cut)
 
phon_d %>% 
  filter(Focus == "PhonologicalFoil") %>% 
  left_join(minp1) %>% 
  ggplot() + 
    aes(x = Time, y = plogis(empirical_logit(PhonologicalFoil, Unrelated))) + 
    geom_line(aes(group = ResearchID), alpha = .2) +
    stat_smooth(aes(color = Cut), se = FALSE) +
    facet_grid(. ~ Study)  + 
    ggtitle("To phon foil by minimal pairs")

phon_d %>% 
  filter(Focus == "Target") %>% 
  left_join(minp1) %>% 
  ggplot() + 
    aes(x = Time, y = Prop) + 
    geom_line(aes(group = ResearchID), alpha = .2) +
    stat_smooth(aes(color = Cut), se = FALSE) +
    facet_grid(. ~ Study) + 
   ggtitle("Prop to target by minimal pairs")

# phon_d %>% 
#   filter(Focus == "Target") %>% 
#   left_join(minp1) %>% 
#   ggplot() + 
#     aes(x = Time, y = plogis(empirical_logit(Target, Unrelated))) + 
#     geom_line(aes(group = ResearchID), alpha = .2) +
#     stat_smooth(aes(color = Cut), se = FALSE) +
#     facet_grid(. ~ Study)

# phon_d %>% 
#   filter(Focus == "PhonologicalFoil") %>% 
#   left_join(minp1) %>% 
#   ggplot() + 
#     aes(x = Time) + 
#     # geom_line(aes(group = ResearchID), alpha = .2) +
#     stat_smooth(
#       aes(color = Cut, y = plogis(empirical_logit(Target, PhonologicalFoil))), 
#       se = FALSE) +
#     stat_smooth(
#       aes(color = Cut, y = plogis(empirical_logit(Target, Unrelated))), 
#       se = FALSE, linetype = "dashed") +
#     facet_grid(Cut ~ Study)

# phon_d %>% 
#   filter(Focus == "Target") %>% 
#   left_join(minp1) %>% 
#   ggplot() + 
#     aes(x = Time, y = Prop) + 
#     geom_line(aes(group = ResearchID), alpha = .2) +
#     stat_smooth(aes(color = Cut), se = FALSE) +
#     facet_grid(. ~ Study)


evt1 <- readr::read_csv("./data-raw/test_scores.csv") %>% 
  select(Study, ResearchID, EVT_Standard) %>% 
  filter(Study == "TimePoint1") %>% 
  mutate(EVT = ntile(EVT_Standard, 4)) %>% 
  select(-Study)

# gfta1 <- readr::read_csv("./data-raw/scores_for_participant_summary.csv") %>% 
#   select(Study, ResearchID, GFTA_Standard) %>% 
#   filter(Study == "TimePoint1") %>% 
#   mutate(GFTA = ntile(GFTA_Standard, 4)) %>% 
#   select(-Study)


phon_d %>% 
  filter(Focus == "PhonologicalFoil") %>% 
  left_join(evt1) %>% 
  ggplot() + 
    aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
    geom_line(aes(group = ResearchID), alpha = .2) + 
    stat_smooth(aes(color = factor(EVT)), se = FALSE) +
    facet_grid(. ~ Study)

# phon_d %>% 
#   filter(Focus == "PhonologicalFoil") %>% 
#   left_join(gfta1) %>% 
#   ggplot() + 
#     aes(x = Time, y = empirical_logit(PhonologicalFoil, Unrelated)) + 
#     geom_line(aes(group = ResearchID), alpha = .2) + 
#     stat_smooth(aes(color = factor(GFTA)), se = FALSE) +
#     facet_grid(. ~ Study)



semy_d %>% 
  filter(Focus == "SemanticFoil") %>% 
  left_join(evt1) %>% 
  ggplot() + 
    aes(x = Time, y = empirical_logit(SemanticFoil, Unrelated)) + 
    geom_line(aes(group = ResearchID), alpha = .2) + 
    stat_smooth(aes(color = factor(EVT)), se = FALSE) +
    facet_grid(. ~ Study)

semy_d %>% 
  filter(Focus == "SemanticFoil") %>% 
  left_join(minp1) %>% 
  ggplot() + 
    aes(x = Time, y = empirical_logit(SemanticFoil, Unrelated)) + 
    geom_line(aes(group = ResearchID), alpha = .2) + 
    stat_smooth(aes(color = Cut), se = FALSE) +
    facet_grid(. ~ Study)

# m <- glmer(
#   cbind(PhonologicalFoil, Unrelated) ~ 
#     (ot1 + ot2 + ot3) * Study + 
#     (ot1 + ot2 + ot3 | ResearchID), 
#   family = binomial,
#   data = d_m)
# summary(m)
```

```{r, eval = FALSE, echo = FALSE}
library(lme4)
fx <- . %>% 
  glmer(
    cbind(PhonologicalFoil, Unrelated) ~
      (ot1 + ot2 + ot3) +
      (ot1 + ot2 + ot3 | ResearchID),
    family = binomial,
    data = .)

by_study <- d_m %>% 
  tidyr::nest(-Study) %>% 
  mutate(model = purrr::map(data, fx))


lapply(by_study$model, summary)

by_study <- by_study %>% 
  mutate(data = purrr::map2(model, data, broom::augment))



data
size = 10
tidyr::unnest(by_study, data) %>% 
  sample_n_of(12, ResearchID) %>% 
  ggplot() + 
  aes(x = BinTime, y = .fitted, color = Study) + 
  geom_point() + 
  geom_line(aes(group = interaction(ResearchID, Study))) + 
  facet_wrap("ResearchID")
```

## Interim summary

* Visual evidence that the semantic foil and phonological foil become more 
  relevant (compared to unrelated foil) each year. 
* Our previous distinction between strong and weak foils still applies, 
  although it might be better to exclude only the (a priori) weakest foils, 
  like the rime phonological foils.
