Method {#aim2-method}
=======================================================================

```{r include = FALSE}
knitr::read_chunk("./helpers.R")
if (interactive()) source("./helpers.R")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r helpers, message = FALSE, warning = FALSE}
```

```{r include = FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

Data collection for this experiment occurred during the same
longitudinal study as the familiar word recognition experiment of Aim 1.
Thus, this experiment used the same participants, same stimulus
preparation, and same general experimental procedure that were reported
in detail in [Chapter \@ref(aim1-method)](#aim1-method).


Mispronunciation task
------------------------------------------------------------------------

This experiment is an adaptation of the mispronunciation detection task
by @WhiteMorgan2008 and @MPPaper. In the experiment, two images are
presented onscreen—a familiar object and an unfamiliar object—and the
child hears a prompt to view one of the images. In the *correct
pronunciation* (or *real word*) and *mispronunciation* conditions, the
child hears either the familiar word (e.g., *soup*) or a one-feature
mispronunciation of the first consonant of the target word (*shoup*).
These conditions are designed to test whether children map
mispronunciations to novel words. To encourage fast referent selection,
there were also trials in a *nonword* condition where the label was an
unambiguous novel word (e.g., *cheem* presented with images of a bed and
a novel-looking pastry mixer). Each nonword was constructed to match the
phonotactic probability of one of the mispronunciations. 
Figure \@ref(fig:`r sample-mp-screen`) shows the displays used in two
trials. Importantly, within a block of trials, the child never hears
both the correct and mispronounced forms of the same word. A child
hearing "duck" then a few trials later hearing "guck" would provide a
basis of comparison so that the child can decide that "guck" is probably
not "duck"---our design avoided this situation.

(ref:sample-mp-screen-cap) Example displays for (*left*) a trial in
which *duck* is mispronounced as "guck"and (*right*) a trial in which
the nonword "cheem" is presented.

```{r sample-mp-screen, fig.cap = "(ref:sample-mp-screen-cap)", echo = FALSE, out.width = "100%"}
library(magick)
dir_screens <- "./misc/mp-screens/TimePoint1/actual/"

i1 <- dir_screens %>% 
  file.path("Block1_03_MP_bull2_duck2_ImageR_guk.png") %>% 
  image_read() %>% 
  image_scale("x400")

i2 <- dir_screens %>% 
  file.path("Block1_14_nonsense_bed2_mixer2_ImageL_Cim.png") %>% 
  image_read() %>% 
  image_scale("x400")

image_append(c(i1, i2))
```

<!-- (Maybe explain why the nonword condition give children the license to -->
<!-- interpret a mispronunciation as a nonword.) -->
<!-- So, children sometimes heard correct productions that can be mapped to familiar -->
<!-- objects and sometimes heard flagrant nonwords that could be quickly associated -->
<!-- to unfamilar objects. Both of these behaviors are encouraged by the experiment. -->

In a block of the experiment, there were 12 trials each from the correct
production, mispronunciation, and nonword conditions, and children
received two blocks of the task. A complete list of the items used in
the experiment over the three years of the study is included in
[Appendix \@ref(mp-experiment-items)](#mp-experiment-items).


Visual stimuli
------------------------------------------------------------------------

The images used in the experiment consisted of color photographs on gray
backgrounds. As in the familiar word recognition, these images were
piloted in two preschool classrooms. Piloting confirmed that children
consistently used the same label for familiar objects and did not
consistently use the same label for novel/unfamiliar objects.


Data screening {#aim2-screening}
------------------------------------------------------------------------





