Items used in Study 1 {#vw-experiment-items}
========================================================================

```{r include = FALSE, warning = FALSE}
knitr::read_chunk("./helpers.R")
if (interactive()) source("./helpers.R")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r helpers, include = FALSE}
```

```{r vw-items, include = FALSE}
trial_info <- bind_rows(
  readr::read_csv("data-raw/rwl_timepoint1_trials.csv.gz"),
  readr::read_csv("data-raw/rwl_timepoint2_trials.csv.gz"),
  readr::read_csv("data-raw/rwl_timepoint3_trials.csv.gz")) %>%
  select(
    Study,
    TrialID,
    Target = WordTarget,
    PhonologicalFoil = WordPhonologicalFoil,
    SemanticFoil = WordSemanticFoil,
    Unrelated = WordUnrelated)

## There was a block at year one where the wrong unrelated was used.
## See the items with 15 trials each. We will exclude them.
trials_to_drop <- trial_info %>%
  count(Study, Target, PhonologicalFoil, SemanticFoil, Unrelated) %>%
  filter(n <= 15)

words <- trial_info %>%
  distinct(Target, PhonologicalFoil, SemanticFoil, Unrelated) %>%
  anti_join(
    trials_to_drop,
    by = c("Target", "PhonologicalFoil", "SemanticFoil", "Unrelated")) %>% 
  group_by(Target) %>% 
  mutate(Unrelated = paste(sort(Unrelated), collapse = "/")) %>% 
  distinct() %>% 
  ungroup() %>% 
  setNames(c("Target", "Phonological", "Semantic", "Unrelated")) %>% 
  arrange(Target)

# aim1_stim$good_phon is a constant defined in helpers.R
phono_foils <- split(words, words$Target %in% aim1_stim$good_phon) %>%
  setNames(c("weak_foil", "strong_foil"))

# aim1_stim$good_semy is a constant defined in helpers.R
semy_foils <- split(words, words$Target %in% aim1_stim$good_semy) %>%
  setNames(c("weak_foil", "strong_foil"))
```

Table \@ref(tab:aim1-all-items) lists the items used for the visual world
experiment in Study 1. Each row of the table represents a set of four
images used in a trial. There were two blocks of trials with different
images and trial orderings. For the two unrelated foils with more than
one word listed, the two foils were used in different blocks. That is,
*pear* had *ring* as its unrelated competitor in one block and *vase* in
the other block. This happened due to a design oversight.

```{r aim1-all-items, echo = FALSE}
c1 <- "Sets of four images used for the Visual World Experiment."
if (knitr::is_latex_output()) {
  knitr::kable(
    words,
    format = "latex",
    booktabs = TRUE,
    linesep = c("", "", "", "\\addlinespace"),
    caption = c1)
} else { 
  knitr::kable(
    words,
    caption = c1)
}
```


For the analysis of phonological competitors, I only used trials where
the target and the phonological foil shared the same syllable onset
(Table \@ref(tab:phonological-competitor-items)). For the analysis of
semantic competitors, I only used trials where the target and the
semantic foil belonged to the same category 
(Table \@ref(tab:semantic-competitor-items)).

```{r phonological-competitor-items, echo = FALSE}
c2 <- 
  "Items used for the analysis of phonological versus unrelated competitors."

if (knitr::is_latex_output()) {
  phono_foils$strong_foil %>%
    select(-Semantic) %>% 
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      linesep = c("", "", "", "\\addlinespace"),
      caption = c2)
} else { 
  phono_foils$strong_foil %>%
    select(-Semantic) %>% 
    knitr::kable(
      caption = c2)
}
```

```{r semantic-competitor-items, echo = FALSE}
c3 <- 
  "Items used for the analysis of semantic versus unrelated competitors."

if (knitr::is_latex_output()) {
  semy_foils$strong_foil %>%
    select(-Phonological) %>% 
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      linesep = c("", "", "", "\\addlinespace"),
      caption = c3)
} else { 
  semy_foils$strong_foil %>%
    select(-Phonological) %>% 
    knitr::kable(
      caption = c3)
}
```

