\backmatter

# Colophon {-}

## Debug info

```{r}
str(list(html = is_html_output(), latex = is_latex_output(),
         word = is_word_output(), width = options("width")[[1]]))

devtools::session_info()

last_four_commits <- git2r::commits(git2r::repository("."), n = 4)
msgs <- lapply(last_four_commits, methods::show)
```



```{r include = FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', "lme4", 
  "rstanarm", "dplyr", "ggplot2", "littlelisteners", "tristan", 
  "bayesplot", "tjmisc", "rlang"), './assets/packages.bib')

# dir.create("./docs/")
# dir.create("./docs/assets/")
# file.copy(
#   list.files("./assets/", full.names = TRUE), 
#   file.path("./docs/assets", list.files("./assets/")), 
#   overwrite = TRUE)
```

Built with love using `r papaja::cite_r("./assets/packages.bib")`.


***

This is the original colophon from the huskydown package. I need to
reword and note my modifications.

> This document is set in [EB
> Garamond](https://github.com/georgd/EB-Garamond), [Source Code
> Pro](https://github.com/adobe-fonts/source-code-pro/) and
> [Lato](http://www.latofonts.com/lato-free-fonts/). The body text is
> set at 11pt with $\familydefault$.

> It was written in R Markdown and $\LaTeX$, and rendered into PDF
> using [huskydown](https://github.com/benmarwick/huskydown) and
> [bookdown](https://github.com/rstudio/bookdown).

> This document was typeset using the XeTeX typesetting system, and the
> [University of Washington Thesis
> class](http://staff.washington.edu/fox/tex/) class created by Jim Fox.
> Under the hood, the [University of Washington Thesis LaTeX
> template](https://github.com/UWIT-IAM/UWThesis) is used to ensure that
> documents conform precisely to submission standards. Other elements of
> the document formatting source code have been taken from the [Latex,
> Knitr, and RMarkdown templates for UC Berkeley's graduate
> thesis](https://github.com/stevenpollack/ucbthesis), and [Dissertate:
> a LaTeX dissertation template to support the production and
> typesetting of a PhD dissertation at Harvard, Princeton, and
> NYU](https://github.com/suchow/Dissertate)

> The source files for this thesis, along with all the data files, have
> been organised into an R package, xxx, which is available at
> <https://github.com/xxx/xxx>. A hard copy of the thesis can be found
> in the University of Washington library.
